---
title: "Generate Fake Input Data For An AQoL-6D Mapping Study"
author: "Matthew Hamilton"
date: "11/08/2020"
output: html_document
---

# Introduction
This program generates a purely synthetic (i.e. fake - no trace of any real records) population that is reasonably representative of the input data we used for the utility mapping study described in the article https://doi.org/10.1101/2021.07.07.21260129. 

No access to the real data is required in order to use this program - it is based on summary statistics (e.g. means and standard deviations of variables, correlation matrices). It should be noted however, that a different (and simpler) workflow can be implemented when you do have access to the source dataset (for example, by using the `syn` function from the `synthpop` package). 

The output of this program is very similar but not identical to a fake dataset created by an earlier version of this program and which is saved in the "ymh_clinical_dict_r3.RDS" file from the https://doi.org/10.7910/DVN/HJXYKQ data repository. 

# Install required R packages
If you do not have the following packages already installed, uncomment and run the following lines.

```{r echo = F}
# install.packages("faux")
# devtools::install_github("ready4-dev/ready4) 
# devtools::install_github("ready4-dev/youthvars) 
# devtools::install_github("ready4-dev/scorz) 
# devtools::install_github("ready4-dev/specific") 
# devtools::install_github("ready4-dev/TTU")
# devtools::install_github("ready4-dev/youthu")
```

Load the ready4 framework package.

```{r, message=FALSE}
library(ready4)
```

# Specify parameters to generate outcome fake data

## AQoL item response parameters
The first set of input data are the proportions for each allowed response for each of the twenty AQOL-6D questions at both baseline and followup.

```{r}
aqol_items_prpns_tbs_ls <- list(bl_answer_props_tb = tibble::tribble(
    ~Question, ~Answer_1, ~Answer_2, ~Answer_3, ~Answer_4, ~Answer_5, ~Answer_6,
    "Q1", 0.35, 0.38, 0.16, 0.03, NA_real_,100, # Check item 5 in real data.
    "Q2", 0.28, 0.38, 0.18, 0.08, 0.04,100,
    "Q3", 0.78, 0.18, 0.03, 0.01, 0.0, 100,
    "Q4", 0.64, 0.23, 0.09, 0.0, 100, NA_real_,
    "Q5", 0.3, 0.48, 0.12, 0.05, 100, NA_real_,
    "Q6", 0.33, 0.48, 0.15, 100, NA_real_,NA_real_,
    "Q7", 0.44, 0.27, 0.11, 100, NA_real_, NA_real_,
    "Q8", 0.18, 0.29, 0.23, 0.21, 100, NA_real_,
    "Q9", 0.07, 0.27, 0.19, 0.37, 100, NA_real_,
    "Q10", 0.04, 0.15, 0.4, 0.25, 100, NA_real_,
    "Q11", 0.03, 0.13, 0.52, 0.25, 100, NA_real_,
    "Q12", 0.06, 0.21, 0.25, 0.34, 100, NA_real_,
    "Q13", 0.05, 0.25, 0.31, 0.28, 100, NA_real_,
    "Q14", 0.05, 0.3, 0.34, 0.25, 100, NA_real_,
    "Q15", 0.57, 0.25, 0.12, 100, NA_real_,NA_real_,
    "Q16", 0.48, 0.42, 0.06, 100, NA_real_, NA_real_,
    "Q17", 0.44, 0.3, 0.16, 0.07, 100, NA_real_,
    "Q18", 0.33, 0.38, 0.25, 0.04, 0.0, 100,
    "Q19", 0.33, 0.49, 0.16, 0.02, 0.0, 100,
    "Q20", 0.67, 0.21, 0.02, 100, NA_real_,NA_real_),
    fup_answer_props_tb = tibble::tribble(
    ~Question, ~Answer_1, ~Answer_2, ~Answer_3, ~Answer_4, ~Answer_5, ~Answer_6,
    "Q1", 0.51, 0.33, 0.12, 0.02, NA_real_, 100,
    "Q2", 0.36, 0.38, 0.16, 0.06, 0.02,100,
    "Q3", 0.81, 0.15, 0.04, 0.00, 0.0, 100,
    "Q4", 0.73, 0.18, 0.09, 0.0, 100, NA_real_,
    "Q5", 0.36, 0.42, 0.12, 0.05, 100, NA_real_,
    "Q6", 0.48, 0.40, 0.11, 100, NA_real_,NA_real_,
    "Q7", 0.57, 0.25, 0.09, 100, NA_real_, NA_real_,
    "Q8", 0.31, 0.33, 0.17, 0.12, 100, NA_real_,
    "Q9", 0.13, 0.35, 0.19, 0.23, 100, NA_real_,
    "Q10", 0.1, 0.21, 0.43, 0.16, 100, NA_real_,
    "Q11", 0.06, 0.25, 0.48, 0.18, 100, NA_real_,
    "Q12", 0.08, 0.27, 0.26, 0.25, 100, NA_real_,
    "Q13", 0.07, 0.37, 0.31, 0.19, 100, NA_real_,
    "Q14", 0.08, 0.37, 0.34, 0.15, 100, NA_real_,
    "Q15", 0.62, 0.23, 0.09, 100, NA_real_,NA_real_,
    "Q16", 0.52, 0.40, 0.06, 100, NA_real_, NA_real_,
    "Q17", 0.51, 0.28, 0.15, 0.06, 100, NA_real_,
    "Q18", 0.37, 0.35, 0.25, 0.03, 0.0, 100,
    "Q19", 0.43, 0.40, 0.16, 0.01, 0.0, 100,
    "Q20", 0.77, 0.21, 0.02, 100, NA_real_,NA_real_)) %>%
  youthvars::make_complete_prpns_tbs_ls()
```

## Outcome variable correlation parameters

First we specify the names of variables we will be creating as outcome variables.

```{r}
var_names_chr <- c("aqol6d_total_w","phq9_total","bads_total",
                   "gad7_total","oasis_total","scared_total","k6_total")
```

The next step is to specify the correlations between outcome variables (variables assumed to be ordered as in previous step) at baseline and follow-up timepoints.

```{r}
cor_mat_ls <- list(matrix(c(1,-0.78,0.72,-0.67,-0.71,-0.65,-0.67,
                               NA,1,-0.73,0.69,0.66,0.63,0.71,
                               NA,NA,1,-.57,-0.64,-0.57,-0.65,
                               NA,NA,NA,1,0.74,0.70,0.63,
                               NA,NA,NA,NA,1,0.7,0.59,
                               NA,NA,NA,NA,NA,1,0.55,
                               NA,NA,NA,NA,NA,NA,1),7,7),
                    matrix(c(1,-0.81,0.72,-0.71,-0.73,-0.64,-0.68,
                        NA,1,-0.72,0.69,0.68,0.61,0.68,
                        NA,NA,1,-0.59,-0.61,-0.51,-0.61,
                        NA,NA,NA,1,0.75,0.71,0.6,
                        NA,NA,NA,NA,1,0.68,0.59,
                        NA,NA,NA,NA,NA,1,0.52,
                        NA,NA,NA,NA,NA,NA,1),7,7)) 
```

We now specify the univariate distribution parameters for each of the outcome variables.

```{r, results='hide', message=FALSE}
synth_data_spine_ls <- list(cor_mat_ls = cor_mat_ls,
                            nbr_obs_dbl = c(1068,643),
                            timepoint_nms_chr = c("BL","FUP"),
                            means_ls = list(c(0.6,12.8,78.2, 10.4,8.1,34.2,12.2),
                                            c(0.7,9.8,89.4, 7.9,6.3,28.8,9.8)),
                            sds_ls = list(c(0.2,6.6,24.8,5.7,4.7,17.9,5.8),
                                          c(0.2,6.5,24.4,5.5,4.3,17.8,5.9)),
                            missing_ls = list(c(0,4,10,6,7,7,4),
                                              c(0,5,2,2,1,2,2)),
                            min_max_ls = list(c(0.03,1),
                                              c(0,27),
                                              c(0,150),
                                              c(0,21),
                                              c(0,20),
                                              c(0,82),
                                              c(0,24)),
                            discrete_lgl = c(F,rep(T,6)),
                            var_names_chr = var_names_chr,
                            aqol_tots_var_nms_chr = c(cumulative = "aqol6d_total_c",
                                                      weighted = "aqol6d_total_w")) 
```

# Generate fake data

## Create fake outcome variable datasets
We now use the parameters we have just specified to create baseline and follow-up datasets with fake data for our nominated outcome variables.

```{r}
aqol_scores_pars_ls <- list(means_dbl = c(44.5,40.6), 
                            sds_dbl = c(9.9,9.8),
                            corr_dbl = -0.95)
aqol6d_adol_pop_tbs_ls <- aqol_items_prpns_tbs_ls %>%
  scorz::make_aqol6d_adol_pop_tbs_ls(aqol_scores_pars_ls = aqol_scores_pars_ls,
                                     series_names_chr =  c("bl_outcomes_tb",
                                                           "fup_outcomes_tb"),
                                     synth_data_spine_ls = synth_data_spine_ls,
                                     temporal_cors_ls = list(aqol6d_total_w = 0.85))
```

## Create fake descriptive variables
We now specify the names and statistical parameters of the variables we will be using in descriptive statistics. For this analysis we are not interested in capturing the joint distribution between these variables, so we only use univariate parameters.

```{r}
descriptives_BL_tb <- tibble::tibble(fkClientID = aqol6d_adol_pop_tbs_ls$bl_outcomes_tb$fkClientID,
                                     round = c(1) ,
                                     d_age = rnorm(1068,18.1,3.3) %>% 
                                       purrr::map_dbl(~min(.x,25) %>% 
                                                        max(12)),
                                     d_gender = c(rep(1,653),
                                                  rep(2,359),
                                                  rep(3,39),
                                                  rep(NA_real_,17)) %>% 
                                       specific::scramble_xx() %>%
                                       factor(labels = c("Female","Male","Other")),
                                     d_sexual_ori_s = c(rep(1,738),
                                                        rep(2,289),
                                                        rep(NA_real_,41)) %>% 
                                       scramble_xx() %>%
                                       factor(labels = c("Straight","Other")),
                                     Region = c(rep(1,671),
                                                rep(2,397)) %>% 
                                       specific::scramble_xx() %>%
                                       factor(labels = c("Metro","Regional")),
                                     CALD = c(rep(T,759),
                                              rep(F,169),
                                              rep(NA,140)) %>% 
                                       specific::scramble_xx(),
                                     d_studying_working = c(rep(1,405),
                                                            rep(2,167),
                                                            rep(3,305),
                                                            rep(4,159),
                                                            rep(NA_real_,32)) %>% 
                                       specific::scramble_xx() %>% 
                                       factor(labels = c("Studying only",
                                                         "Working only",
                                                         "Studying and working",
                                                         "Not studying or working")),
                                     c_p_diag_s = c(rep(1,182),
                                                    rep(2,264),
                                                    rep(3,332),
                                                    rep(4,237),
                                                    rep(NA_real_,53)) %>% 
                                       specific::scramble_xx() %>%
                         factor(labels = c("Depression", "Anxiety","Depression and Anxiety", "Other")),
                         c_clinical_staging_s = c(rep(1,625),
                                                  rep(2,326),
                                                  rep(3,86),
                                                  rep(NA_real_,31)) %>% 
                           specific::scramble_xx() %>%
                           factor(labels = c("0-1a","1b","2-4")),
                         c_sofas = c(rnorm(1068-30,65.2,9.5),
                                     rep(NA_real_,30)) %>% 
                           purrr::map_dbl(~min(.x,100) %>% 
                                            max(0)) %>% 
                           specific::scramble_xx(),
                         s_centre = NA_character_, 
                         d_agegroup = NA_character_, 
                         d_sex_birth_s = NA_character_, 
                         d_country_bir_s = NA_character_,
                         d_ATSI = NA_character_,
                         d_english_home = NA, 
                         d_english_native = NA, 
                         d_relation_s = c(rep(1,325),
                                          rep(2,426),
                                          rep(3,286),
                                          rep(NA_real_,31)) %>% 
                           specific::scramble_xx() %>%
                           factor(labels = c("REPLACE_ME_1",
                                             "REPLACE_ME_2",
                                             "REPLACE_ME_3")))  %>%
  dplyr::mutate(d_sex_birth_s = dplyr::case_when(is.na(d_gender) ~ NA_integer_,
                                                 as.integer(d_gender) %in% 
                                                   c(1L,2L) & 
                                                   runif(1068)>0.995 ~ as.integer(d_gender) %>%
                                                   purrr::map_int(~ ifelse(is.na(.x), 
                                                                           .x, 
                                                                           switch(.x,2L,1L,3L))),
                                                 as.integer(d_gender) == 3 ~ sample(c(1L,2L), 
                                                                                    1068, 
                                                                                    replace = T),
                                                 TRUE ~ as.integer(d_gender)
                                                 ) %>%
                  factor(labels = c("Female","Male")))
descriptives_FUP_tb <- descriptives_BL_tb %>% 
  dplyr::filter(fkClientID %in% 
                  aqol6d_adol_pop_tbs_ls$fup_outcomes_tb$fkClientID) %>%
  dplyr::mutate(round = 2,
                d_age = d_age + 0.25,
                Region = Region %>% 
                  specific::randomise_changes_in_fct_lvls(0.98),
                d_studying_working = d_studying_working %>%
                  specific::randomise_changes_in_fct_lvls(0.9),
                c_p_diag_s = c_p_diag_s %>% 
                  specific::randomise_changes_in_fct_lvls(0.90),
                c_clinical_staging_s = c_clinical_staging_s %>% 
                  specific::randomise_changes_in_fct_lvls(0.8),
                c_sofas = c_sofas + rnorm(643,4.7,10) %>% 
                         purrr::map_dbl(~min(.x,100) %>% max(0)))
bl_tb <- dplyr::inner_join(descriptives_BL_tb,
                           aqol6d_adol_pop_tbs_ls$bl_outcomes_tb) 
fup_tb <- dplyr::inner_join(descriptives_FUP_tb,
                            aqol6d_adol_pop_tbs_ls$fup_outcomes_tb)
```

We make some adjustments to ensure that the `c_sofas` variable is correlated with our `aqol6d_total_w` variable at both baseline and follow-up.

```{r}
bl_tb <- bl_tb %>%
  dplyr::mutate(c_sofas = faux::rnorm_pre(bl_tb$aqol6d_total_w %>% 
                                            as.vector(), 
                                          mu = 65.2, 
                                          sd = 9.5, 
                                          r = 0.5, 
                                          empirical = T) %>% 
                  purrr::map_dbl(~min(.x,100) %>% max(0)))
fup_tb <- fup_tb %>%
  dplyr::mutate(c_sofas = faux::rnorm_pre(fup_tb$aqol6d_total_w %>% 
                                            as.vector(), 
                                          mu = 69.9, 
                                          sd = 10, 
                                          r = 0.5, 
                                          empirical = T) %>% 
                  purrr::map_dbl(~min(.x,100) %>% max(0)))
```

## Add fake outcome variables to fake descriptive variables.

```{r}
composite_tb <- dplyr::bind_rows(bl_tb, fup_tb) %>%
  dplyr::mutate(d_age = floor(d_age)) %>%
  dplyr::mutate(d_gender = d_gender %>% as.character() %>%
                  purrr::map_chr(~ifelse(.x=="Other",
                                         sample(c("Genderqueer/gender nonconforming/agender",
                                                              "Transgender"),1),
                                         .x)),
                s_centre = Region %>% as.character() %>%
                  purrr::map_chr(~ifelse(.x=="Metro",
                                         sample(c("Canberra","Southport","Knox"),1),
                                         "Regional Centre")),
                d_country_bir_s = CALD %>%
                  purrr::map_chr(~ifelse(.x,
                                         "Other",
                                         "Australia")), 
                       d_ATSI = CALD %>%
                  purrr::map_chr(~ifelse(.x,
                                         "Yes",
                                         "No")),
                       d_english_home = CALD %>%
                  purrr::map_chr(~ifelse(.x,
                                         "No",
                                         "Yes")), 
                       d_english_native = CALD %>%
                  purrr::map_chr(~ifelse(.x,
                                         "No",
                                         "Yes"))
                ) %>%
  dplyr::select(-CALD) %>%
  dplyr::select(-Region)
composite_tb <- composite_tb %>%
  dplyr::select(-setdiff(names(composite_tb)[startsWith(names(composite_tb),
                                                        "aqol6d_")],
                         names(composite_tb)[startsWith(names(composite_tb),
                                                        "aqol6d_q")]))
composite_tb <- composite_tb %>%
  dplyr::mutate(c_sofas = as.integer(round(c_sofas,0))) %>%
  dplyr::mutate(round = factor(round, labels = c("Baseline",
                                                 "Follow-up"))) %>%
  dplyr::mutate(d_relation_s = dplyr::case_when(d_relation_s %in% 
                                                  c("REPLACE_ME_1","REPLACE_ME_2") ~ 
                                                  "Not in a relationship",
                                                T ~ "In a relationship")) %>%
  youthu::add_dates_from_dstr(bl_start_date_dtm = Sys.Date() - lubridate::days(600),##
                              bl_end_date_dtm = Sys.Date() - lubridate::days(420),
                              duration_args_ls = list(a = 60, b = 140, mean = 90, sd = 10),
                              duration_fn = truncnorm::rtruncnorm,
                              date_var_nm_1L_chr = "d_interview_date") %>%
  dplyr::select(-duration_prd) %>%
  youthvars::transform_raw_ds_for_analysis() %>%
  dplyr::rename(phq9_total = PHQ9,
                bads_total = BADS,
                gad7_total = GAD7,
                oasis_total = OASIS,
                scared_total = SCARED,
                k6_total = K6,
                c_sofas = SOFAS) %>%
  dplyr::select(-c("d_agegroup","Gender", "CALD", "Region"))
```

<!-- Next we write a copy of these input parameters and the synthetic population dataset as CSV files. -->

```{r}
# dss_tb <- write_results_to_csv(synth_data_spine_ls,
#                                output_dir_1L_chr = "Data") 
# write.csv(composite_tb, 
#           file = paste0("Data/fake_pop_tb.csv"),
#           row.names = F)
# dss_tb <- tibble::add_case(dss_tb,
#                            ds_obj_nm_chr = "fake_pop_tb",
#                            title_chr = "Synthetic population representative of study participants but containing no trace of source records. The synthetic population was constructed using correlation matrices and summary statistics from the source dataset.")
```

```{r}
# NOT FOR INCLUSION IN VIGNETTE
# ready4::write_to_dv_with_wait(dss_tb,
#                                dv_nm_1L_chr = "ready4models",
#                                ds_url_1L_chr = "https://doi.org/10.7910/DVN/GRZRY5",
#                                parent_dv_dir_1L_chr = "../../../../../../Data/Dataverse",
#                                paths_to_dirs_chr = "Data",
#                                inc_fl_types_chr = ".csv")
```

```{r}
# if(!dir.exists("Data"))
#   dir.create("Data")
# saveRDS(composite_tb,"Data/fake_pop_tb.rds") 
```
