---
title: "Analyse, report and share"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analyse, report and share}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
\blandscape
<!---BLOCK_LANDSCAPE_START--->

```{r echo = TRUE }
library(magrittr)
```

# Input parameters

## Bibliograhic data
We begin by specifying the authorship data we wish to attach to all reports that we generate.

```{r }
authors_tb <- ready4show::authors_tb
```
```{r authorsds, eval = knitr::is_html_output(), results='asis'}
authors_tb %>%
  ready4show::print_table(output_type_1L_chr = "HTML",
                          caption_1L_chr = "Authors table",
                          mkdn_tbl_ref_1L_chr = "tab:authorsds")
```
```{r}
institutes_tb <- ready4show::institutes_tb
```
```{r institutesds, eval = knitr::is_html_output(), results='asis'}
institutes_tb %>%
  ready4show::print_table(output_type_1L_chr = "HTML",
                          caption_1L_chr = "Author institutions table",
                          mkdn_tbl_ref_1L_chr = "tab:institutesds")
```

We combine the data about authors with other bibliographic information.

```{r}
header_yaml_args_ls <- TTU::make_header_yaml_args_ls(authors_tb = authors_tb,
                                                     institutes_tb = institutes_tb,
                                                     title_1L_chr = "A hypothetical study using fake data for instructional purposes only",
                                                     keywords_chr = c("this","is","a","replication","using","fake","data","do", "not","cite"))
```

## Report formatting
We add parameters relating to the desired output format of the reports we will be producing.

```{r }
output_format_ls <- TTU::make_output_format_ls(manuscript_outp_1L_chr = "Word",
                                               manuscript_digits_1L_int = 2L,
                                               supplementary_outp_1L_chr = "PDF",
                                               supplementary_digits_1L_int = 2L)
```

## Relative paths
We next create an object that specifies the relative locations of the input data and the intended destination for analysis outputs and reports. The default settings of the `make_path_params_ls` function will write all output into a new directory, created one level up from the current working directory.

```{r}
path_params_ls <- TTU::make_path_params_ls("fake_data.rds")
```

## Dataset
As this is an illustrative example, we first must create a fake dataset (if using real data, skip this step).

```{r message=FALSE}
ds_tb <- readRDS(url("https://dataverse.harvard.edu/api/access/datafile/4749888"))
```
```{r inputds, eval = knitr::is_html_output(), results='asis'}
ds_tb %>%
    head() %>%
  ready4show::print_table(output_type_1L_chr = "HTML",
                          caption_1L_chr = "Input dataset",
                          mkdn_tbl_ref_1L_chr = "tab:inputds")
```

A data dictionary must also be supplied for the dataset. The dictionary must be of class `ready4_dictionary` from the `ready4use` package.

```{r}
dictionary_tb <- TTU::make_eq5d_ds_dict(ds_tb)
```
```{r dictionary, eval = knitr::is_html_output(), results='asis'}
dictionary_tb %>%
  ready4show::print_table(output_type_1L_chr = "HTML",
                          caption_1L_chr = "Data dictionary",
                          mkdn_tbl_ref_1L_chr = "tab:dictionary")
```

We note our use of synthetic data by creating an object `use_fake_data_1L_lgl` and setting it to `TRUE`. For real world application - set this variable to `FALSE`.

```{r }
use_fake_data_1L_lgl <-  TRUE
```

We describe the features of our dataset that are most relevant to the analyses we are planning to undertake. Note all, Multi-Attribute Utility Instrument (MAUI) question variables must start with a common prefix, which needs to be passed to the `maui_item_pfx_1L_chr` argument. The dataset does not need to include variables for total health utility scores (weighted and unweighted), as these variables will be computed during the analysis. However, you can supply the names you wish assigned to these variables once they are computed using the `utl_wtd_var_nm_1L_chr` and `utl_unwtd_var_nm_1L_chr` arguments.

```{r echo = TRUE}
ds_descvs_ls <- TTU::make_ds_descvs_ls(candidate_predrs_chr = c("k10_int","psych_well_int"),
                     cohort_descv_var_nms_chr = c("d_age", "Gender", "d_relation_s","d_sexual_ori_s", "Region", "CALD", "d_studying_working"),
                     dictionary_tb = dictionary_tb, 
                     id_var_nm_1L_chr = "uid", 
                     msrmnt_date_var_nm_1L_chr = "data_collection_dtm",
                     round_var_nm_1L_chr = "Timepoint", 
                     round_vals_chr = c("BL", "FUP"),
                     maui_item_pfx_1L_chr = "eq5dq_", 
                     utl_wtd_var_nm_1L_chr = "EQ5D_total_dbl", 
                     utl_unwtd_var_nm_1L_chr = "EQ5d_cumulative_dbl")
```

## Candidate predictors
We create a lookup table with metadata on the dataset variables that we will be exploring as candidate predictors.

```{r}
predictors_lup <- TTU::TTU_predictors_lup(TTU::make_pt_TTU_predictors_lup(short_name_chr = ds_descvs_ls$candidate_predrs_chr,
                                              long_name_chr = c("Kessler Psychological Distress - 10 Item Total Score",
                                                   "Overall Wellbeing Measure (Winefield et al. 2012)"),
                                              min_val_dbl = c(10,18),
                                              max_val_dbl = c(50,90),
                                              class_chr = "integer",
                                              increment_dbl = 1,
                                              class_fn_chr = "as.integer",
                                              mdl_scaling_dbl = 0.01,
                                              covariate_lgl = F))
```

## MAUI parameters
We also need to provide information specific to the Multi-Attribute Utility Instrument (MAUI) used to collect the data from which health utility will be derived. If our source dataset does not include a pre-calculated weighted utility variable, we must supply a function to calculate this variable using the `maui_scoring_fn` argument. Note if specifying such a function, it must:
 - include identical arguments as in the below example (including names and order), even if all arguments are not required; and
 - also calculate an unweighted score that is a simple sum of all maui item question responses (e.g. the last three lines of the example `maui_scoring_fn`).

```{r}
maui_params_ls <- TTU::make_maui_params_ls(maui_itm_short_nms_chr = c("Mobility", "Self-care", "Activities","Pain","Anxiety"),
                                      maui_scoring_fn = function(data_tb,
                                             maui_item_pfx_1L_chr,
                                             id_var_nm_1L_chr, 
                                             utl_wtd_var_nm_1L_chr,
                                             utl_unwtd_var_nm_1L_chr){
                    require(eq5d)
                    data_tb %>% 
                      dplyr::rename_with(~stringr::str_replace(.x,maui_item_pfx_1L_chr,""),
                                         dplyr::starts_with(maui_item_pfx_1L_chr)) %>%
                      dplyr::mutate(`:=`(!!rlang::sym(utl_wtd_var_nm_1L_chr), 
                                         eq5d::eq5d(., country="UK", version = "5L", type = "CW"))) %>%
                      dplyr::rename_with(~paste0(maui_item_pfx_1L_chr,.x),c("MO","SC","UA","PD","AD")) %>%
                      dplyr::mutate(`:=`(!!rlang::sym(utl_unwtd_var_nm_1L_chr),                                          rowSums(dplyr::across(dplyr::starts_with(maui_item_pfx_1L_chr))))) %>%
                      dplyr::filter(!is.na(!!rlang::sym(utl_unwtd_var_nm_1L_chr)))
                    })
```

## Candidate model types
We next create a lookup table of the candidate model types we wish to explore. A template look-up table is available as part of the `TTU` package, but this may need need to be adapted (e.g. in the below example, we alter the start values of some models) for optimal use with your input data.

```{r}
mdl_types_lup <- TTU::mdl_types_lup %>%
  dplyr::mutate(start_chr = dplyr::case_when(short_name_chr %in% c("GLM_BNL_LGT","GLM_BNL_CLL") ~ c("0.5, -0.05"),
                                             T ~ start_chr))
  
```

```{r mdltypeslup, eval = knitr::is_html_output(), results='asis'}
mdl_types_lup %>%
  ready4show::print_table(output_type_1L_chr = "HTML",
                          caption_1L_chr = "Candidate model types lookup table",
                          mkdn_tbl_ref_1L_chr = "tab:mdltypeslup")
```

## Analysis parameters
We first combine our candidate model types lookup table with parameters specific to the analyses to be run to compare the performance of each model.

```{r}
mdl_smry_ls <- TTU::make_mdl_smry_ls(mdl_types_lup = mdl_types_lup,
                                     folds_1L_int = 10L,
                                     max_nbr_of_boruta_mdl_runs_int = 300L)
```

```{r echo = TRUE }
analysis_core_params_ls <- TTU::make_analysis_core_params_ls(ds_descvs_ls = ds_descvs_ls,
                                                             mdl_smry_ls = mdl_smry_ls,
                                                             output_format_ls = output_format_ls,
                                                             predictors_lup = predictors_lup,
                                                             use_fake_data_1L_lgl = use_fake_data_1L_lgl,
                                                             control_ls = list(adapt_delta = 0.99))
```

## Reporting details

```{r echo = TRUE }
paths_ls <- TTU::write_main_oupt_dir(path_params_ls, 
                                     use_fake_data_1L_lgl = use_fake_data_1L_lgl)
```

## Output repositories
Provide details of dataverse dataset(s) to which results will be posted. If you do not permissions for any dataverse datasets, set `dv_ls <- NULL`.

```{r echo = TRUE }
dv_ls <- list(primary_dv_chr = c("fakes","https://doi.org/10.7910/DVN/612HDC"))
```

# Primary Analysis

## Consolidate required parameters
```{r}
prmry_analysis_params_ls <- TTU::make_prmry_analysis_params_ls(analysis_core_params_ls,
                                                          candidate_covar_nms_chr = c("d_sex_birth_s", "d_age",  "d_sexual_ori_s", "d_relation_s", "d_studying_working"),
                                                          ds_tb = ds_tb, 
                                                          path_params_ls = path_params_ls,
                                                          maui_params_ls = maui_params_ls)
```

## Run analysis

```{r echo = TRUE }
TTU::write_report(params_ls = prmry_analysis_params_ls,
                  paths_ls = paths_ls,
                  rprt_nm_1L_chr = "Main_Analysis_Rprt",
                  abstract_args_ls = NULL,
                  header_yaml_args_ls = header_yaml_args_ls)
```

## Report results

```{r echo = TRUE }
TTU::write_mdl_smry_rprt(header_yaml_args_ls,
                    paths_ls = paths_ls,
                    path_params_ls = path_params_ls,
                    use_fake_data_1L_lgl = use_fake_data_1L_lgl,
                    output_format_ls = output_format_ls)
# TTU::write_rprt_with_rcrd(path_to_outp_fl_1L_chr = paste0(paths_ls$output_data_dir_1L_chr,"/I_ALL_OUTPUT_.RDS"), 
#                      paths_ls = paths_ls,
#                      header_yaml_args_ls = header_yaml_args_ls,
#                      use_fake_data_1L_lgl = use_fake_data_1L_lgl,
#                      subtitle_1L_chr = "Results Report 1: TTU Models (Primary Analysis)",
#                      rprt_subtitle_1L_chr = "Methods Report 2: Reporting Program (Primary Analysis).",
#                      rprt_nm_1L_chr = "TS_TTU_Mdls_Smry",
#                      rcrd_nm_1L_chr = "Write_Rprt_Rcrd",
#                      output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
#                      rprt_output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
#                      nbr_of_digits_1L_int = output_format_ls$supplementary_digits_1L_int,
#                      abstract_args_ls = NULL,
#                      rcrd_rprt_append_ls = path_params_ls[1:2])
```

## Share (de-confidentialised) results

```{r echo = TRUE }
if(!is.null(dv_ls)){
  TTU::write_study_outp_ds(dv_ls,
                           output_format_ls = output_format_ls,
                           path_params_ls = path_params_ls,
                           paths_ls = paths_ls)
  # params_ls <- list(dv_ds_nm_and_url_chr = dv_ls$primary_dv_chr,
  #                   dv_mdl_desc_1L_chr = "This is a time series transfer to utility model designed for use with the youthu R package.",
  #                   inc_fl_types_chr = ".pdf",
  #                   nbr_of_digits_1L_int = output_format_ls$supplementary_digits_1L_int,
  #                   output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
  #                   purge_data_1L_lgl = FALSE,
  #                   subtitle_1L_chr = "Methods Report 3: Sharing Program (Primary Analysis)",
  #                   use_fake_data_1L_lgl = use_fake_data_1L_lgl) %>%
  #   append(path_params_ls[1:2])
  # params_ls %>%
  #   TTU::write_report(paths_ls = paths_ls,
  #                     rprt_nm_1L_chr = "Share_Outp_Rprt",
  #                     abstract_args_ls = NULL,
  #                     header_yaml_args_ls = header_yaml_args_ls,
  #                     rprt_lup = TTU::transform_rprt_lup(TTU::rprt_lup, 
  #                                                        add_suplry_rprt_1L_lgl = F,
  #                                                        add_sharing_rprt_1L_lgl = T))
  # ready4use::write_fls_to_dv_ds(dss_tb = tibble::tibble(ds_obj_nm_chr = "Share_Outp_Rprt",
  #                                                       title_chr = params_ls$subtitle_1L_chr),
  #                               dv_nm_1L_chr = dv_ls$primary_dv_chr[1],
  #                               ds_url_1L_chr = dv_ls$primary_dv_chr[2],
  #                               parent_dv_dir_1L_chr = paths_ls$dv_dir_1L_chr,
  #                               paths_to_dirs_chr = paths_ls$reports_dir_1L_chr,
  #                               inc_fl_types_chr = params_ls$inc_fl_types_chr,
  #                               paths_are_rltv_1L_lgl = F)
}
```

# Secondary Analysis A (Anxiety + Depression)

```{r echo = TRUE }
# reference_1L_int <- 1
# scndry_paths_ls <- TTU::write_scndry_analysis_dir(paths_ls,
#                                              reference_1L_int = reference_1L_int)
```

## Run analysis

```{r echo = TRUE }
TTU::write_scndry_analysis(analysis_core_params_ls = analysis_core_params_ls,
                           candidate_covar_nms_chr = c("BADS", "SOFAS", "c_p_diag_s", "c_clinical_staging_s",
                                                       "d_age",  "d_sex_birth_s", "d_sexual_ori_s", "d_country_bir_s", "d_relation_s",
                                                       "d_studying_working"),
                           candidate_predrs_chr = c("SCARED","OASIS","GAD7"),
                           path_params_ls = path_params_ls,
                           prefd_covars_chr = "BADS",
                           reference_1L_int = 1,
                           header_yaml_args_ls = header_yaml_args_ls,
                           paths_ls = paths_ls)
```

## Report results

```{r echo = TRUE }
TTU::write_mdl_smry_rprt(header_yaml_args_ls,
                    paths_ls = paths_ls,
                    path_params_ls = path_params_ls,
                    use_fake_data_1L_lgl = use_fake_data_1L_lgl,
                    output_format_ls = output_format_ls,
                    reference_1L_int = 1)
# TTU::write_rprt_with_rcrd(path_to_outp_fl_1L_chr = here::here(paths_ls$path_from_top_level_1L_chr,
#                                                               paths_ls$write_to_dir_nm_1L_chr,
#                                                               paste0("secondary_",reference_1L_int),
#                                                               "Output","I_ALL_OUTPUT_.RDS"),
#                           paths_ls = scndry_paths_ls,
#                           header_yaml_args_ls = header_yaml_args_ls,
#                           use_fake_data_1L_lgl = use_fake_data_1L_lgl,
#                           subtitle_1L_chr = "Results Report 2: TTU Models (Secondary Analysis A)",
#                           rprt_subtitle_1L_chr = "Methods Report 5: Reporting Program (Secondary Analysis A).",
#                           rprt_nm_1L_chr = "TS_TTU_Mdls_Smry",
#                           rcrd_nm_1L_chr = "Write_Rprt_Rcrd",
#                           output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
#                           rprt_output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
#                           nbr_of_digits_1L_int = output_format_ls$supplementary_digits_1L_int,
#                           abstract_args_ls = NULL,
#                           rcrd_rprt_append_ls = path_params_ls[1:2],
#                           main_rprt_append_ls = list(existing_predrs_ls = readRDS(paste0(paths_ls$output_data_dir_1L_chr,
#                                                                              "/I_ALL_OUTPUT_.RDS")) %>% 
#                                           purrr::pluck("predr_vars_nms_ls")))
```

## Share (de-confidentialised) results

```{r echo = TRUE }
if(!is.null(dv_ls$secondary_1_dv_chr)){
    TTU::write_study_outp_ds(dv_ls,
                             output_format_ls = output_format_ls,
                             path_params_ls = path_params_ls,
                             paths_ls = paths_ls,
                             reference_1L_int = 1)
  # params_ls <- list(dv_ds_nm_and_url_chr = dv_ls$secondary_1_dv_chr,#
  #                             dv_mdl_desc_1L_chr = "This is a time series transfer to utility model designed for use with the youthu R package.",
  #                             inc_fl_types_chr = ".pdf",
  #                             nbr_of_digits_1L_int = output_format_ls$supplementary_digits_1L_int,
  #                             output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
  #                             purge_data_1L_lgl = FALSE,
  #                             rprt_lup = TTU::rprt_lup,#
  #                             subtitle_1L_chr = "Methods Report 6: Sharing Program (Secondary Analysis A)",#
  #                             transform_paths_ls = list(fn = transform_paths_ls_for_scndry, #TTU::
  #                                                       args_ls = list(reference_1L_int = reference_1L_int,
  #                                                                      remove_prmry_1L_lgl = T)),#
  #                             use_fake_data_1L_lgl = use_fake_data_1L_lgl) %>%
  #   append(path_params_ls[1:2])
  #  
  #   TTU::write_report(params_ls = params_ls,
  #                     paths_ls = scndry_paths_ls[names(scndry_paths_ls) != "prmry_analysis_dir_nm_1L_chr"],#
  #                     rprt_nm_1L_chr = "Share_Outp_Rprt",
  #                     abstract_args_ls = NULL,
  #                     header_yaml_args_ls = header_yaml_args_ls,
  #                     rprt_lup = TTU::transform_rprt_lup(TTU::rprt_lup, 
  #                                                        add_suplry_rprt_1L_lgl = F,
  #                                                        add_sharing_rprt_1L_lgl = T))
  #   ready4use::write_fls_to_dv_ds(dss_tb = tibble::tibble(ds_obj_nm_chr = "Share_Outp_Rprt",
  #                                                       title_chr = params_ls$subtitle_1L_chr),
  #                               dv_nm_1L_chr = dv_ls$primary_dv_chr[1],#
  #                               ds_url_1L_chr = dv_ls$primary_dv_chr[2],#
  #                               parent_dv_dir_1L_chr = paths_ls$dv_dir_1L_chr,
  #                               paths_to_dirs_chr = paths_ls$reports_dir_1L_chr,
  #                               inc_fl_types_chr = params_ls$inc_fl_types_chr,
  #                               paths_are_rltv_1L_lgl = F)
}
```


# Secondary Analysis B (SOFAS)

## Run analysis

```{r echo = TRUE }
#reference_1L_int <- 2
# scndry_paths_ls <- TTU::write_scndry_analysis_dir(paths_ls,
#                                              reference_1L_int = reference_1L_int)
TTU::write_scndry_analysis(analysis_core_params_ls = analysis_core_params_ls,
                           candidate_covar_nms_chr = c("d_sex_birth_s", "c_p_diag_s", "c_clinical_staging_s", "d_age",  
                                                       "d_sexual_ori_s", "d_country_bir_s", "d_relation_s", "d_studying_working"),
                           candidate_predrs_chr = "SOFAS",
                           header_yaml_args_ls = header_yaml_args_ls,
                           path_params_ls = path_params_ls,
                           paths_ls = paths_ls,
                           prefd_covars_chr = NULL,
                           reference_1L_int = 2)
```

## Report results

```{r echo = TRUE }
TTU::write_mdl_smry_rprt(header_yaml_args_ls,
                    paths_ls = scndry_paths_ls,
                    path_params_ls = path_params_ls,
                    use_fake_data_1L_lgl = use_fake_data_1L_lgl,
                    output_format_ls = output_format_ls,
                    reference_1L_int = 2)
# TTU::write_rprt_with_rcrd(path_to_outp_fl_1L_chr = here::here(paths_ls$path_from_top_level_1L_chr,
#                                                               paths_ls$write_to_dir_nm_1L_chr,
#                                                               paste0("secondary_",reference_1L_int),
#                                                               "Output","I_ALL_OUTPUT_.RDS"),
#                           paths_ls = scndry_paths_ls,
#                           header_yaml_args_ls = header_yaml_args_ls,
#                           use_fake_data_1L_lgl = use_fake_data_1L_lgl,
#                           subtitle_1L_chr = "Results Report 3: TTU Models (Secondary Analysis B)",
#                           rprt_subtitle_1L_chr = "Methods Report 8: Reporting Program (Secondary Analysis B).",
#                           rprt_nm_1L_chr = "TS_TTU_Mdls_Smry",
#                           rcrd_nm_1L_chr = "Write_Rprt_Rcrd",
#                           output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
#                           rprt_output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
#                           nbr_of_digits_1L_int = output_format_ls$supplementary_digits_1L_int,
#                           abstract_args_ls = NULL,
#                           rcrd_rprt_append_ls = path_params_ls[1:2],
#                           main_rprt_append_ls = list(existing_predrs_ls = readRDS(paste0(paths_ls$output_data_dir_1L_chr,
#                                                                                          "/I_ALL_OUTPUT_.RDS")) %>% 
#                                                        purrr::pluck("predr_vars_nms_ls")))
```

## Share (de-confidentialised) results

```{r echo = TRUE }
if(!is.null(dv_ls$secondary_2_dv_chr)){
      TTU::write_study_outp_ds(dv_ls,
                      output_format_ls = output_format_ls,
                      path_params_ls = path_params_ls,
                      paths_ls = paths_ls,
                      reference_1L_int = 2)
  # params_ls <- list(dv_ds_nm_and_url_chr = dv_ls$secondary_2_dv_chr,
  #                             dv_mdl_desc_1L_chr = "This is a time series transfer to utility model designed for use with the youthu R package.",
  #                             inc_fl_types_chr = ".pdf",
  #                             nbr_of_digits_1L_int = output_format_ls$supplementary_digits_1L_int,
  #                             output_type_1L_chr = output_format_ls$supplementary_outp_1L_chr,
  #                             purge_data_1L_lgl = FALSE,
  #                             rprt_lup = TTU::rprt_lup,
  #                             subtitle_1L_chr = "Methods Report 9: Sharing Program (Secondary Analysis B)",
  #                             transform_paths_ls = list(fn = TTU::transform_paths_ls_for_scndry, 
  #                                                       args_ls = list(reference_1L_int = reference_1L_int,
  #                                                                      remove_prmry_1L_lgl = T)),
  #                             use_fake_data_1L_lgl = use_fake_data_1L_lgl) %>%
  #   append(path_params_ls[1:2])
  # 
  #   TTU::write_report(params_ls = params_ls,
  #                     paths_ls = scndry_paths_ls[names(scndry_paths_ls) != "prmry_analysis_dir_nm_1L_chr"],
  #                     rprt_nm_1L_chr = "Share_Outp_Rprt",
  #                     abstract_args_ls = NULL,
  #                     header_yaml_args_ls = header_yaml_args_ls,
  #                     rprt_lup = TTU::transform_rprt_lup(rprt_lup, 
  #                                                        add_suplry_rprt_1L_lgl = F,
  #                                                        add_sharing_rprt_1L_lgl = T))
  #     ready4use::write_fls_to_dv_ds(dss_tb = tibble::tibble(ds_obj_nm_chr = "Share_Outp_Rprt",
  #                                                       title_chr = params_ls$subtitle_1L_chr),
  #                               dv_nm_1L_chr = dv_ls$primary_dv_chr[1],
  #                               ds_url_1L_chr = dv_ls$primary_dv_chr[2],
  #                               parent_dv_dir_1L_chr = paths_ls$dv_dir_1L_chr,
  #                               paths_to_dirs_chr = paths_ls$reports_dir_1L_chr,
  #                               inc_fl_types_chr = params_ls$inc_fl_types_chr,
  #                               paths_are_rltv_1L_lgl = F)
}
```


# Render Manuscript

```{r echo = TRUE }
if(!use_fake_data_1L_lgl){
  var_nm_change_lup <- tibble::tibble(old_nms_chr = c("PHQ9","GAD7"),
                                      new_nms_chr = c("PHQ-9", "GAD-7"))
study_descs_ls <- TTU::make_study_descs_ls(health_utl_nm_1L_chr = "AQol-6D",
                                           time_btwn_bl_and_fup_1L_chr = "three months",
                                           predr_ctgs_ls = list(`psychological distress` = c("K6"),
                                                                depression =  c("BADS","PHQ9"),
                                                                anxiety =  c("GAD7","OASIS","SCARED")))
spine_of_results_ls <- TTU::make_results_ls_spine(output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                                  var_nm_change_lup = var_nm_change_lup,
                                                  study_descs_ls = study_descs_ls,
                                                  nbr_of_digits_1L_int = output_format_ls$manuscript_digits_1L_int)
cs_ts_ratios_tb = tibble::tibble(predr_nm_chr = c("K6","depression measurements", "anxiety measurements"),
                                 ratios_chr = c(paste0("about ",
                                                       round(spine_of_results_ls$mdl_coef_ratios_ls$`psychological distress`,2)),
                                                paste0(round(mean(spine_of_results_ls$mdl_coef_ratios_ls$depression),2)),
                                                paste0(round(min(spine_of_results_ls$mdl_coef_ratios_ls$anxiety),2)," or over")
                                 ))
ctgl_vars_regrouping_ls = list('Primary Diagnosis' = list(anxdpr = list(name_1L_chr = "anxiety/depression",
                                                                          ctgs_chr = c("Anxiety", "Depression", "Depression and Anxiety"))),
                                 'Clinical Stage' = list(early = list(name_1L_chr = "early (prior to first episode of a serious mental disorder) clinical stages",
                                                                      ctgs_chr = c("0-1a","1b"))))
sig_covars_some_predrs_mdls_tb = tibble::tibble(covars_ls = list(c("No other confounding factor"),
                                                                                  c("sex at birth"),
                                                                                                     c("primary diagnosis", "clinical staging","age")),
                                                                 predrs_mdls_ls = list(c("PHQ-9"), c("K6"),c("anxiety and depression measurements other than PHQ-9")),
                                                                 sig_thresh_dbl = c(NA_real_,0.01,NA_real_),
                                                                 assn_strgth_chr = c(NA_character_,NA_character_,"weakly"))
results_ls <- TTU::make_results_ls(spine_of_results_ls,
                                   cs_ts_ratios_tb = cs_ts_ratios_tb,
                                   ctgl_vars_regrouping_ls = ctgl_vars_regrouping_ls,
                                   sig_covars_some_predrs_mdls_tb = sig_covars_some_predrs_mdls_tb,
                                   sig_thresh_covars_1L_chr = "0.005")
saveRDS(results_ls,paste0(paths_ls$output_data_dir_1L_chr,"/results_ls.RDS"))
  rmarkdown::render("AQoL_VIH/AQoL_VIH.Rmd",
                    output_format = NULL,
                    params = list(figures_in_body_lgl = F,
                                  output_type_1L_chr = "Word",
                                  results_ls = results_ls,
                                  tables_in_body_lgl = F),
                    output_file = paste0("AQoL_VIH", ".docx"),
                    output_dir = paths_ls$reports_dir_1L_chr)
}
```

# Purge dataset copies
```{r echo = TRUE }
TTU::write_to_delete_ds_copies(paths_ls)
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->
