---
title: "Reporting Workflow, AQoL-6D Clinical Population Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reporting Workflow, AQoL-6D Clinical Population Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

\blandscape
<!---BLOCK_LANDSCAPE_START--->

This vignette is an example of implementing of analysis, reporting and sharing workflow to develop transfer to AQoL-6D health utility models. Some of the initial steps in this example are described in more detail in the [EQ-5D example](CSP_EQ5D_TTU.html).
```{r echo = TRUE, message=FALSE}
library(TTU)
```

# Input parameters

## Reporting parameters

### Bibliograhic data
We begin by specifying the authorship and other bibliographic data that we wish to attach to all reports that we generate.

```{r}
header_yaml_args_ls <- make_header_yaml_args_ls(authors_tb = ready4show::authors_tb,
                                                institutes_tb = ready4show::institutes_tb,
                                                title_1L_chr = "A hypothetical study using fake data for instructional purposes only",
                                                keywords_chr = c("this","is","a","replication","using","fake","data","do", "not","cite"))
```

### Report formatting
We add parameters relating to the desired output format of the reports we will be producing.

```{r }
output_format_ls <- make_output_format_ls(manuscript_outp_1L_chr = "Word",
                                               manuscript_digits_1L_int = 2L,
                                               supplementary_outp_1L_chr = "PDF",
                                               supplementary_digits_1L_int = 2L)
```

## Data parameters

### Dataset
We read in our study dataset (in this case we are using fake data).

```{r message=FALSE}
ds_tb <- youthvars::replication_popl_tb %>% 
            youthvars::transform_raw_ds_for_analysis() 
```

```{r }
use_fake_data_1L_lgl <-  TRUE
```

### Dataset metadata
We describe the features of our dataset that are most relevant to the analyses we are planning to undertake. 

```{r echo = TRUE}
ds_descvs_ls <- make_ds_descvs_ls(candidate_predrs_chr = c("K6","PHQ9"),#
                                  cohort_descv_var_nms_chr = c("d_age","d_relation_s",
                                                               "d_studying_working",
                                                               "c_p_diag_s","c_clinical_staging_s"),
                                  dictionary_tb = youthvars::make_final_rpln_ds_dict(), 
                                  id_var_nm_1L_chr = "fkClientID", 
                                  msrmnt_date_var_nm_1L_chr = "d_interview_date",
                                  round_var_nm_1L_chr = "round", 
                                  round_vals_chr = c("Baseline", "Follow-up"),
                                  maui_item_pfx_1L_chr = "aqol6d_q", 
                                  utl_wtd_var_nm_1L_chr = "aqol6d_total_w", 
                                  utl_unwtd_var_nm_1L_chr = "aqol6d_total_c")
```

### Candidate predictors metadata
We create a lookup table with metadata on the dataset variables that we specified in the `candidate_predrs_chr` element of `ds_descvs_ls` as our candidate predictors, as well as the preferred covariates that we will specify later in the `make_valid_params_ls_ls` function.

```{r}
predictors_lup <- make_pt_TTU_predictors_lup(short_name_chr = c(ds_descvs_ls$candidate_predrs_chr, "SOFAS"),
                                              long_name_chr = c("K6 total score", "PHQ9 total score", "SOFAS total score"),
                                              min_val_dbl = 0,
                                              max_val_dbl = c(24,27,100),
                                              class_chr = "integer",
                                              increment_dbl = 1,
                                              class_fn_chr = c("youthvars::youthvars_k6",
                                                               "youthvars::youthvars_phq9",
                                                               "youthvars::youthvars_sofas"),
                                              mdl_scaling_dbl = 0.01,
                                              covariate_lgl = F) %>%
  TTU_predictors_lup()
```

## Analysis parameters

### Multi-Attribute Utility Instrument (MAUI) parameters
We also need to provide information specific to the MAUI used to collect the data from which health utility will be derived.

```{r}
maui_params_ls <- make_maui_params_ls(maui_domains_pfcs_1L_chr = "vD",
                                      maui_itm_short_nms_chr = c("Household tasks", "Getting around","Morbility","Self care","Enjoy close rels","Family rels", "Community involvement","Despair","Worry", "Sad", "Agitated","Energy level","Control", "Coping","Frequency of pain", "Degree of pain","Pain interference","Vision", "Hearing","Communication"),
                                      maui_scoring_fn = youthvars::add_adol6d_scores,
                                      short_and_long_nm = c("AQoL-6D",
                                                            "Assessment of Quality of Life - Six Dimension"),
                                      utl_min_val_1L_dbl = 0.03)
```

## Core parameters
We create a summary object that contains the core parameters that will be common to most of the analyses we are planning to run.

```{r echo = TRUE }
analysis_core_params_ls <- make_analysis_core_params_ls(ds_descvs_ls = ds_descvs_ls,
                                                        output_format_ls = output_format_ls,
                                                        predictors_lup = predictors_lup,
                                                        candidate_covar_nms_chr = c("d_age", "SOFAS",
                                                                                    "c_p_diag_s",                                                                                    "c_clinical_staging_s", 
                                                                                    "d_relation_s",
                                                                                    "d_studying_working"),
                                                        prefd_covars_chr = "SOFAS",
                                                        prefd_mdl_types_chr = c("GLM_GSN_LOG",
                                                                                "OLS_CLL"),
                                                        use_fake_data_1L_lgl = use_fake_data_1L_lgl)
```

## Path parameters
We next create an object that specifies the relative locations of the input data and the intended destination for analysis outputs and reports. The default settings of the `make_path_params_ls` function will write all output into a new directory, created one level up from the current working directory.

```{r, warning=F, message=F, eval=F}
path_params_ls <- make_path_params_ls(use_fake_data_1L_lgl = use_fake_data_1L_lgl,
                                      write_new_dir_1L_lgl = T)
```

## Validate parameters
A list of valid input values for our primary analysis is now constructed, principally using the objects created in the preceding steps. The `make_valid_params_ls_ls` checks the naming conventions used in some variables of interest and where necessary (for consistency with reporting templates) modifies the names of these variables.

```{r eval = F}
params_ls_ls <- make_valid_params_ls_ls(analysis_core_params_ls,
                                              ds_tb = ds_tb, 
                                              maui_params_ls = maui_params_ls,
                                              path_params_ls = path_params_ls)
```

# Run analysis
## Primary analysis
All analytic steps for our primary analysis are executed with the following function call.

```{r echo = TRUE, eval=FALSE}
write_report(params_ls = params_ls_ls$params_ls,
             paths_ls = path_params_ls$paths_ls,
             rprt_nm_1L_chr = "AAA_PMRY_ANLYS_MTH",
             abstract_args_ls = NULL,
             header_yaml_args_ls = header_yaml_args_ls)
```

## Secondary Analyses 
We can specify supplementary analyses (that apply the same preferred model types as the primary analysis to different combinations of candidate predictors and covariates) by creating a new predictors lookup table and making a call to the `write_scndry_analysis` function.

```{r echo = TRUE, eval=FALSE}
write_scndry_analysis(valid_params_ls_ls = params_ls_ls,
                      candidate_covar_nms_chr = ds_descvs_ls %>%                                                                             purrr::pluck("cohort_descv_var_nms_chr"),
                      candidate_predrs_chr = c("SOFAS"),
                      header_yaml_args_ls = header_yaml_args_ls,
                      path_params_ls = path_params_ls,
                      prefd_covars_chr = NA_character_,
                      reference_1L_int = 1)
  
```

# Report results
As we have undertaken more than one analysis, we need to supply integer values to the `reference_int` argument of the `write_mdl_smry_rprt` function for each analysis that we wish to generate a report for. The value `0` corresponds to the primary analysis, with each subsequent integer corresponding to a supplementary analysis.

```{r echo = TRUE, eval=FALSE }
rprt_lups_ls <- write_mdl_smry_rprt(header_yaml_args_ls,
                                    path_params_ls = path_params_ls,
                                    use_fake_data_1L_lgl = use_fake_data_1L_lgl,
                                    output_format_ls = output_format_ls,
                                    reference_int = 0:1,
                                    use_shareable_mdls_1L_lgl = T)
```

# Share results
Share the results created in the previous step via an online repository. 

Note: you will need to replace the values assigned to the `dv_ds_nm_and_url_chr` argument with the details of dataverse datasets for which you have write permissions - the values supplied in the below call will not work for you. If you do not have write permissions for a dataverse dataset, use `dv_ds_nm_and_url_chr = NULL`. If you are writing results to a dataverse dataset, you will also need to have created a dataverse API key and stored the API key and server values in your local environment. To see how to do this, visit: https://github.com/IQSS/dataverse-client-r

The dataset populated by the below call can be viewed at: https://doi.org/10.7910/DVN/D74QMP
```{r echo = TRUE, eval=FALSE }
dv_ds_nm_and_url_chr <- c("fakes", # Name of dataverse containing dataset - Replace
                          "https://doi.org/10.7910/DVN/D74QMP") # Dataset DOI - Replace
write_study_outp_ds(dv_ds_nm_and_url_chr = dv_ds_nm_and_url_chr,
                    rprt_lups_ls = rprt_lups_ls,
                    output_format_ls = output_format_ls,
                    path_params_ls = path_params_ls,
                    use_fake_data_1L_lgl = use_fake_data_1L_lgl)

```

# Create manuscript
The first step to creating a manuscript that provides the scientific summary of the study is to provide some metadata about the study itself.

```{r}
study_descs_ls <- make_study_descs_ls(coi_1L_chr = "None declared.",
                                      ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
                                      funding_1L_chr = "The study was funded by Generous Benefactor.",
                                      params_ls_ls = params_ls_ls,
                                      sample_desc_1L_chr = "The study sample was recruited from young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
                                      time_btwn_bl_and_fup_1L_chr = "three months")
```

If you want the manuscript to refer to some of the candidate predictors by different names than that provided in the `short_name_chr` column of the `predictors_lup` object defined earlier, you can create a table of name correspondences.

```{r}
var_nm_change_lup <- tibble::tibble(old_nms_chr = c("PHQ9","GAD7"),
                                    new_nms_chr = c("PHQ-9", "GAD-7"))
```

```{r echo = FALSE, eval=FALSE }
spine_of_results_ls <- make_results_ls_spine(output_format_ls,
                                             params_ls_ls = params_ls_ls,
                                             path_params_ls = path_params_ls,
                                             study_descs_ls = study_descs_ls,
                                             var_nm_change_lup = var_nm_change_lup)

```
```{r}
sig_covars_some_predrs_mdls_tb <- tibble::tibble(covars_ls = list(c("No other confounding factor"),
                                                                 c("sex at birth"),
                                                                 c("primary diagnosis", 
                                                                   "clinical staging","age")),
                                                                 predrs_mdls_ls = list(c("either predictor"), 
                                                                                       c("K6"),
                                                                                       c("anxiety and depression measurements other than PHQ-9")
                                                                                       ),
                                                                 sig_thresh_dbl = c(NA_real_,
                                                                                    0.01,
                                                                                    NA_real_),
                                                                 assn_strgth_chr = c(NA_character_,NA_character_,"weakly"
                                                                                     ))
results_ls <- make_results_ls(spine_of_results_ls,
                              sig_covars_some_predrs_mdls_tb = sig_covars_some_predrs_mdls_tb,
                              sig_thresh_covars_1L_chr = "0.005")
```

```{r echo = FALSE, eval=FALSE }
saveRDS(results_ls,paste0(path_params_ls$paths_ls$output_data_dir_1L_chr,"/results_ls.RDS"))
  rmarkdown::render("AQoL_VIH/AQoL_VIH.Rmd",
                    output_format = NULL,
                    params = list(figures_in_body_lgl = F,
                                  output_type_1L_chr = "Word",
                                  results_ls = results_ls,
                                  tables_in_body_lgl = F),
                    output_file = paste0("AQoL_VIH", ".docx"),
                    output_dir = path_params_ls$paths_ls$reports_dir_1L_chr)
# }
```

# Purge dataset copies
All remaining local copies (but not the original version) of the study dataset are deleted from the workspace.

```{r echo = TRUE, eval=FALSE }
write_to_delete_ds_copies(path_params_ls$paths_ls)
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->
