---
title: "Reporting Workflow, EQ5D General Population Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reporting Workflow, EQ5D General Population Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

\blandscape
<!---BLOCK_LANDSCAPE_START--->
Note, this vignette uses fake data - it is for illustrative purposes only and should not be used to inform decision making.

The steps in this reporting workflow should only be undertaken once an optimal set of input values have been identified by an [initial exploratory analysis](Model_TTU.html). Many of the steps in this example are in common with those of the [AQoL-6D vignette](CSP_AQOL6D_TTU.html), and are therefore described with minimal explanation here.

```{r echo = TRUE, message=FALSE}
library(eq5d)
library(TTU)
```

# Input parameters

## Reporting parameters

### Bibliograhic data
```{r}
header_yaml_args_ls <- make_header_yaml_args_ls(authors_tb = ready4show::authors_tb,
                                                institutes_tb = ready4show::institutes_tb,
                                                title_1L_chr = "A hypothetical study using fake data for instructional purposes only",
                                                keywords_chr = c("this","is","a","replication","using","fake","data","do", "not","cite"))
```

### Report formatting
```{r }
output_format_ls <- make_output_format_ls(manuscript_outp_1L_chr = "PDF",
                                          manuscript_digits_1L_int = 2L,
                                          supplementary_outp_1L_chr = "PDF",
                                          supplementary_digits_1L_int = 2L)
```

## Data parameters

### Dataset

```{r message=FALSE}
ds_tb <- readRDS(url("https://dataverse.harvard.edu/api/access/datafile/4750597")) 
```

The first few records of the dataset are as follows.

```{r inputds, echo=F, eval = knitr::is_html_output(), results='asis'}
ds_tb %>%
    head() %>%
  ready4show::print_table(output_type_1L_chr = "HTML",
                          caption_1L_chr = "Input dataset",
                          mkdn_tbl_ref_1L_chr = "tab:inputds")
```

### Dataset metadata
We describe the features of our dataset that are most relevant to the analyses we are planning to undertake. Note all, Multi-Attribute Utility Instrument (MAUI) question variables must start with a common prefix, which needs to be passed to the `maui_item_pfx_1L_chr` argument. The dataset does not need to include variables for total health utility scores (weighted and unweighted), as these variables will be computed during the analysis. However, you can supply the names you wish assigned to these variables once they are computed using the `utl_wtd_var_nm_1L_chr` and `utl_unwtd_var_nm_1L_chr` arguments.

```{r echo = TRUE, eval = F }
ds_descvs_ls <- make_ds_descvs_ls(candidate_predrs_chr = c("k10_int","psych_well_int"),
                                  candidate_covar_nms_chr = NA_character_,
                                  cohort_descv_var_nms_chr = c("d_age", "Gender", 
                                                               "d_relation_s","d_sexual_ori_s", 
                                                               "Region", "d_studying_working"),
                                  dictionary_tb = make_eq5d_ds_dict(ds_tb), 
                                  id_var_nm_1L_chr = "uid", 
                                  is_fake_1L_lgl = T,
                                  msrmnt_date_var_nm_1L_chr = "data_collection_dtm",
                                  round_var_nm_1L_chr = "Timepoint", 
                                  round_vals_chr = c("BL", "FUP"),
                                  maui_item_pfx_1L_chr = "eq5dq_", 
                                  utl_wtd_var_nm_1L_chr = "EQ5D_total_dbl",
                                  utl_unwtd_var_nm_1L_chr = "EQ5d_cumulative_dbl")
```

### Candidate predictors metadata

```{r eval = F }
predictors_lup <- TTU_predictors_lup(make_pt_TTU_predictors_lup(short_name_chr = ds_descvs_ls$candidate_predrs_chr,
                                              long_name_chr = c("Kessler Psychological Distress - 10 Item Total Score",
                                                   "Overall Psychological Wellbeing (Winefield et al. 2012)"),
                                              min_val_dbl = c(10,18),
                                              max_val_dbl = c(50,90),
                                              class_chr = "integer",
                                              increment_dbl = 1,
                                              class_fn_chr = "as.integer",
                                              mdl_scaling_dbl = 0.01,
                                              covariate_lgl = F))
```

## Analysis parameters

### Multi-Attribute Utility Instrument (MAUI) parameters
If our source dataset does not include a pre-calculated weighted utility variable, we must supply a function to calculate this variable using the `maui_scoring_fn` argument. Note if specifying such a function, it must:

 - include identical arguments as in the below example (including names and order), even if all arguments are not required; and
 - also calculate an unweighted score that is a simple sum of all MAUI item question responses (e.g. the last three lines of the example `maui_scoring_fn`).

```{r eval = F }
maui_params_ls <- make_maui_params_ls(maui_domains_pfcs_1L_chr = "eq5dq_",
                                      maui_itm_short_nms_chr = c("Mobility", "Self-care", "Activities","Pain","Anxiety"),
                                      maui_scoring_fn = function(data_tb,
                                             maui_item_pfx_1L_chr,
                                             id_var_nm_1L_chr, 
                                             utl_wtd_var_nm_1L_chr,
                                             utl_unwtd_var_nm_1L_chr){
                    require(eq5d)
                    data_tb %>% 
                      dplyr::rename_with(~stringr::str_replace(.x,maui_item_pfx_1L_chr,""),
                                         dplyr::starts_with(maui_item_pfx_1L_chr)) %>%
                      dplyr::mutate(`:=`(!!rlang::sym(utl_wtd_var_nm_1L_chr), 
                                         eq5d::eq5d(., country="UK", version = "5L", type = "CW"))) %>%
                      dplyr::rename_with(~paste0(maui_item_pfx_1L_chr,.x),c("MO","SC","UA","PD","AD")) %>%
                      dplyr::mutate(`:=`(!!rlang::sym(utl_unwtd_var_nm_1L_chr),                                          rowSums(dplyr::across(dplyr::starts_with(maui_item_pfx_1L_chr))))) %>%
                      dplyr::filter(!is.na(!!rlang::sym(utl_unwtd_var_nm_1L_chr)))
                    },
                    short_and_long_nm = c("EQ-5D",
                                          "EuroQol - Five Dimension"))
```

## Analysis parameters
Unlike the [AQoL-6D vignette](CSP_AQOL6D_TTU.html), when creating our input parameters list, we need to pass a value to the `control_ls` argument. We discovered this when undertaking the [initial exploratory analysis](Model_TTU.html).
```{r eval = F }
input_params_ls <- make_input_params(ds_tb,
                                     control_ls = list(adapt_delta = 0.99),
                                     ds_descvs_ls = ds_descvs_ls,
                                     dv_ds_nm_and_url_chr = c("fakes", 
                                                              "https://doi.org/10.7910/DVN/612HDC"), 
                                     header_yaml_args_ls = header_yaml_args_ls,
                                     maui_params_ls = maui_params_ls,
                                     output_format_ls = output_format_ls,
                                     predictors_lup = predictors_lup,
                                     prefd_covars_chr = NA_character_)

```


# Run analysis
```{r eval = FALSE}
write_analyses(input_params_ls)
```

# Report results
```{r echo = TRUE, eval=FALSE }
input_params_ls <- write_mdl_smry_rprt(input_params_ls,
                                       use_shareable_mdls_1L_lgl = T)
```

# Share results
```{r echo = TRUE, eval=FALSE }
write_study_outp_ds(input_params_ls)
```
The uploaded files can be viewed at: https://doi.org/10.7910/DVN/612HDC

# Create manuscript

```{r eval = F}
input_params_ls <- make_study_descs_ls(input_params_ls = input_params_ls,
                                       background_1L_chr = "Our study is entirely fictional and has been created to illustrate the generalisability of TTU package functions.",
                                       coi_1L_chr = "None declared.",
                                       conclusion_1L_chr = "If this study was real, the results would be really interesting.",
                                       ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (2222222.2).",
                                       funding_1L_chr = "The study was funded by an science enthusiast.",
                                       sample_desc_1L_chr = "The study sample is fake data that pretends to be Australian young people aged 12 to 25 years.",
                                       time_btwn_bl_and_fup_1L_chr = "four months")
```

```{r eval = F}
results_ls <- write_manuscript(input_params_ls = input_params_ls,
                               write_to_dv_1L_lgl = T)
```

# Purge dataset copies
All remaining local copies (but not the original version) of the study dataset are deleted from the workspace.

```{r echo = TRUE, eval=FALSE }
write_to_delete_ds_copies(path_params_ls$paths_ls)
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->
