---
title: "Reporting Workflow, AQoL-6D Clinical Population Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reporting Workflow, AQoL-6D Clinical Population Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

\blandscape
<!---BLOCK_LANDSCAPE_START--->

This vignette is an example of implementing of analysis, reporting and sharing workflow to develop transfer to AQoL-6D health utility models. Some of the initial steps in this example are described in more detail in the [EQ-5D example](CSP_EQ5D_TTU.html).
```{r echo = TRUE, message=FALSE}
library(magrittr)
library(TTU)
```

# Input parameters

## Reporting parameters

### Bibliograhic data
We begin by specifying the authorship and other bibliographic data that we wish to attach to all reports that we generate.

```{r}
header_yaml_args_ls <- make_header_yaml_args_ls(authors_tb = ready4show::authors_tb,
                                                institutes_tb = ready4show::institutes_tb,
                                                title_1L_chr = "A hypothetical study using fake data for instructional purposes only",
                                                keywords_chr = c("this","is","a","replication","using","fake","data","do", "not","cite"))
```

### Report formatting
We add parameters relating to the desired output format of the reports we will be producing.

```{r }
output_format_ls <- make_output_format_ls(manuscript_outp_1L_chr = "Word",
                                               manuscript_digits_1L_int = 2L,
                                               supplementary_outp_1L_chr = "PDF",
                                               supplementary_digits_1L_int = 2L)
```

## Data parameters

### Dataset
We read in our study dataset (in this case we are using fake data).

```{r message=FALSE}
ds_tb <- youthvars::replication_popl_tb %>% 
            youthvars::transform_raw_ds_for_analysis() 
```

```{r }
use_fake_data_1L_lgl <-  TRUE
```

### Dataset metadata
We describe the features of our dataset that are most relevant to the analyses we are planning to undertake. 

```{r echo = TRUE}
ds_descvs_ls <- make_ds_descvs_ls(candidate_predrs_chr = c("K6","PHQ9"),#
                     cohort_descv_var_nms_chr = c("d_age", "d_relation_s","d_studying_working","c_p_diag_s","c_clinical_staging_s"),
                     dictionary_tb = youthvars::make_final_rpln_ds_dict(), 
                     id_var_nm_1L_chr = "fkClientID", 
                     msrmnt_date_var_nm_1L_chr = "d_interview_date",
                     round_var_nm_1L_chr = "round", 
                     round_vals_chr = c("Baseline", "Follow-up"),
                     maui_item_pfx_1L_chr = "aqol6d_q", 
                     utl_wtd_var_nm_1L_chr = "aqol6d_total_w", 
                     utl_unwtd_var_nm_1L_chr = "aqol6d_total_c")
```

### Candidate predictors metadata
We create a lookup table with metadata on the dataset variables that we specified in the `candidate_predrs_chr` element of `ds_descvs_ls` as our candidate predictors.

```{r}
predictors_lup <- TTU_predictors_lup(make_pt_TTU_predictors_lup(short_name_chr = ds_descvs_ls$candidate_predrs_chr,
                                              long_name_chr = c("K6 total score", "PHQ9 total score"),
                                              min_val_dbl = 0,
                                              max_val_dbl = c(24,27),
                                              class_chr = "integer",
                                              increment_dbl = 1,
                                              class_fn_chr = "as.integer",
                                              mdl_scaling_dbl = 0.01,
                                              covariate_lgl = F))
```

## Analysis parameters

### Multi-Attribute Utility Instrument (MAUI) parameters
We also need to provide information specific to the MAUI used to collect the data from which health utility will be derived.

```{r}
maui_params_ls <- make_maui_params_ls(maui_itm_short_nms_chr = c("Household tasks", "Getting around","Morbility","Self care","Enjoy close rels","Family rels", "Community involvement","Despair","Worry", "Sad", "Agitated","Energy level","Control", "Coping","Frequency of pain", "Degree of pain","Pain interference","Vision", "Hearing","Communication"),
                                      maui_scoring_fn = youthvars::add_adol6d_scores,
                    utl_min_val_1L_dbl = 0.03)
```

## Candidate model types
We combine a lookup table of our candidate model types with parameters specific to the analyses to be run to compare the performance of each model.

```{r}
mdl_smry_ls <- make_mdl_smry_ls(mdl_types_lup = get_cndts_for_mxd_mdls(),
                                     folds_1L_int = 10L,
                                     max_nbr_of_boruta_mdl_runs_int = 300L)
```

We create a summary object that contains the core parameters that will be common to most of the analyses we are planning to run.

```{r echo = TRUE }
analysis_core_params_ls <- make_analysis_core_params_ls(ds_descvs_ls = ds_descvs_ls,
                                                             mdl_smry_ls = mdl_smry_ls,
                                                             output_format_ls = output_format_ls,
                                                             predictors_lup = predictors_lup,
                                                             use_fake_data_1L_lgl = use_fake_data_1L_lgl)
```

## Path parameters
We next create an object that specifies the relative locations of the input data and the intended destination for analysis outputs and reports. The default settings of the `make_path_params_ls` function will write all output into a new directory, created one level up from the current working directory.

```{r, warning=F, message=F, eval=F}
path_params_ls <- make_path_params_ls(use_fake_data_1L_lgl = use_fake_data_1L_lgl,
                                      write_new_dir_1L_lgl = T)
```

## Validate parameters
A list of valid input values for our primary analysis is now constructed, principally using the objects created in the preceding steps. The `make_valid_params_ls_ls` checks the naming conventions used in some variables of interest and where necessary (for consistency with reporting templates) modifies the names of these variables.

```{r eval = F}
valid_params_ls_ls <- make_valid_params_ls_ls(analysis_core_params_ls,
                                                   candidate_covar_nms_chr = c("d_age", "SOFAS", "c_p_diag_s", "c_clinical_staging_s", "d_relation_s", "d_studying_working"),
                                                   ds_tb = ds_tb, 
                                                   maui_params_ls = maui_params_ls,
                                                   path_params_ls = path_params_ls,
                                                   prefd_mdl_types_chr = c("GLM_GSN_LOG",
                                                                           "OLS_CLL"))
```

# Run analysis
## Primary analysis
All analytic steps for our primary analysis are executed with the following function call.

```{r echo = TRUE, eval=FALSE}
write_report(params_ls = valid_params_ls_ls$params_ls,
                  paths_ls = path_params_ls$paths_ls,
                  rprt_nm_1L_chr = "AAA_PMRY_ANLYS_MTH",
                  abstract_args_ls = NULL,
                  header_yaml_args_ls = header_yaml_args_ls)
```

## Secondary Analyses 
We can specify supplementary analyses (that apply the same preferred model types as the primary analysis to different combinations of candidate predictors and covariates) by creating a new predictors lookup table and making a call to the `write_scndry_analysis` function.

```{r echo = TRUE, eval=FALSE}
TTU_predictors_lup(make_pt_TTU_predictors_lup(short_name_chr = "SOFAS",
                                              long_name_chr = c("SOFAS total score"),
                                              min_val_dbl = 0,
                                              max_val_dbl = 100,
                                              class_chr = "integer",
                                              increment_dbl = 1,
                                              class_fn_chr = "youthvars::youthvars_sofas",
                                              mdl_scaling_dbl = 0.01,
                                              covariate_lgl = F)) %>%
  write_scndry_analysis(valid_params_ls_ls = valid_params_ls_ls,
                           candidate_covar_nms_chr = c("d_age", "c_p_diag_s", "c_clinical_staging_s", "d_relation_s", "d_studying_working"),
                           header_yaml_args_ls = header_yaml_args_ls,
                           path_params_ls = path_params_ls,
                           prefd_covars_chr = NA_character_,
                           reference_1L_int = 1)
  
```

# Report results
As we have undertaken more than one analysis, we need to supply integer values to the `reference_int` argument of the `write_mdl_smry_rprt` function for each analysis that we wish to generate a report for. The value `0` corresponds to the primary analysis, with each subsequent integer corresponding to a supplementary analysis.

```{r echo = TRUE, eval=FALSE }
rprt_lups_ls <- write_mdl_smry_rprt(header_yaml_args_ls,
                                    path_params_ls = path_params_ls,
                                    use_fake_data_1L_lgl = use_fake_data_1L_lgl,
                                    output_format_ls = output_format_ls,
                                    reference_int = 0:1,
                                    use_shareable_mdls_1L_lgl = T)

```

# Share results
Share the results created in the previous step via an online repository. 

Note: you will need to replace the values assigned to the `dv_ds_nm_and_url_chr` argument with the details of repositories for which you have write permissions - the values supplied in the below call will not work for you. If you do not have write permissions for a dataverse dataset, use `dv_ds_nm_and_url_chr = NULL`.

The dataset populated by the below call can be viewed at: https://doi.org/10.7910/DVN/JC6PTV
```{r echo = TRUE, eval=FALSE }
write_study_outp_ds(dv_ds_nm_and_url_chr = c("firstbounce", # Name of dataverse containing dataset
                          "https://doi.org/10.7910/DVN/JC6PTV"), # Dataset DOI
                      rprt_lups_ls = rprt_lups_ls,
                      output_format_ls = output_format_ls,
                      path_params_ls = path_params_ls,
                      use_fake_data_1L_lgl = use_fake_data_1L_lgl)

```



```{r echo = FALSE, eval=FALSE }
# Render Scientific Summary
# if(!use_fake_data_1L_lgl){
  # var_nm_change_lup <- tibble::tibble(old_nms_chr = c("k10","psychwell"),
  #                                     new_nms_chr = c("K10", "Winefield wellbeing"))
study_descs_ls <- make_study_descs_ls(health_utl_nm_1L_chr = "EQ-5D",
                                           time_btwn_bl_and_fup_1L_chr = "three months",
                                           predr_ctgs_ls = list(`psychological distress` = c("k10"),
                                                                `psychological wellbeing` =  c("psychwell")))
spine_of_results_ls <- make_results_ls_spine(output_data_dir_1L_chr = path_params_ls$paths_ls$output_data_dir_1L_chr,
                                                  #var_nm_change_lup = var_nm_change_lup,
                                                  study_descs_ls = study_descs_ls,
                                                  nbr_of_digits_1L_int = output_format_ls$manuscript_digits_1L_int)
cs_ts_ratios_tb = tibble::tibble(predr_nm_chr = c("k10","psychwell"),
                                 ratios_chr = c(paste0("about ",
                                                       round(spine_of_results_ls$mdl_coef_ratios_ls$`psychological distress`,2)),
                                                paste0(round(spine_of_results_ls$mdl_coef_ratios_ls$`psychological wellbeing`,2))
                                 ))
# ctgl_vars_regrouping_ls = list('Primary Diagnosis' = list(anxdpr = list(name_1L_chr = "anxiety/depression",
#                                                                           ctgs_chr = c("Anxiety", "Depression", "Depression and Anxiety"))),
#                                  'Clinical Stage' = list(early = list(name_1L_chr = "early (prior to first episode of a serious mental disorder) clinical stages",
#                                                                       ctgs_chr = c("0-1a","1b"))))
sig_covars_some_predrs_mdls_tb = tibble::tibble(covars_ls = list(c("No other confounding factor")
                                                                 # ,c("sex at birth"),c("primary diagnosis", "clinical staging","age")
                                                                 ),
                                                                 predrs_mdls_ls = list(c("either predictor")#, c("K6"),c("anxiety and depression measurements other than PHQ-9")
                                                                                       ),
                                                                 sig_thresh_dbl = c(NA_real_#,0.01,NA_real_
                                                                                    ),
                                                                 assn_strgth_chr = c(NA_character_#,NA_character_,"weakly"
                                                                                     ))
results_ls <- make_results_ls(spine_of_results_ls,
                              cs_ts_ratios_tb = cs_ts_ratios_tb,
                              ctgl_vars_regrouping_ls = NULL,
                              sig_covars_some_predrs_mdls_tb = sig_covars_some_predrs_mdls_tb,
                              sig_thresh_covars_1L_chr = "0.005")
saveRDS(results_ls,paste0(path_params_ls$paths_ls$output_data_dir_1L_chr,"/results_ls.RDS"))
  rmarkdown::render("AQoL_VIH/AQoL_VIH.Rmd",
                    output_format = NULL,
                    params = list(figures_in_body_lgl = F,
                                  output_type_1L_chr = "Word",
                                  results_ls = results_ls,
                                  tables_in_body_lgl = F),
                    output_file = paste0("AQoL_VIH", ".docx"),
                    output_dir = path_params_ls$paths_ls$reports_dir_1L_chr)
# }
```

# Purge dataset copies
All remaining local copies (but not the original version) of the study dataset are deleted from the workspace.

```{r echo = TRUE, eval=FALSE }
write_to_delete_ds_copies(path_params_ls$paths_ls)
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->
