---
title: "Model Transfer to Utility"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Model Transfer to Utility}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(TTU)
```
# Purpose

## Set-up workspace and import data
First, we create a directory in which we will write all output.

```{r}
path_to_write_to_1L_chr <- "Output" 
dir.create(path_to_write_to_1L_chr)
```

Specify the paths to the input data and data dictionary. For this example we are going to use a slightly trimmed down version of the TTU replication dataset and its dictionary[which are described in another vignette article](Replication_DS.html).

```{r}
path_to_inp_data_1L_chr <- "Data" 
dir.create(path_to_inp_data_1L_chr)
write.csv(replication_popl_tb %>% dplyr::select(-BADS,-GAD7, -OASIS,-SCARED),"Data/data.csv", row.names=FALSE, col.names = T)
write.csv(repln_ds_dict_r3,"Data/dictionary.csv", row.names=FALSE)
```

Read the data files into local memory.

```{r message = F}
data_tb <- readr::read_csv("Data/data.csv") 
dictionary_r3 <- readr::read_csv("Data/dictionary.csv") %>% ready4use::ready4_dictionary()
```

## Score utility and summarise meta-data

We now calculate utility scores from study participant responses to the AQoL-6D questionnaire. [More detail about this step is provided in another vignette article](Utility_Scoring.html).

```{r message=FALSE, results='hide', warning=FALSE}
scored_data_tb <- data_tb %>% add_adol6d_scores() %>%
  ready4use::add_labels_from_dictionary(dictionary_r3) 
```

Declare some structural properties of the dataset.

```{r}
ds_smry_ls <- list(candidate_predrs_chr = c("K6","PHQ9"),
                   candidate_covar_nms_chr = c("d_sex_birth_s", "SOFAS", "c_p_diag_s", "c_clinical_staging_s", "d_age",  "d_sexual_ori_s", "d_country_bir_s", "d_relation_s", "d_studying_working"),
                   dep_var_nm_1L_chr = "aqol6d_total_w",
                   id_var_nm_1L_chr = "fkClientID",
                   round_var_nm_1L_chr = "round",
                   round_bl_val_1L_chr = "Baseline")
```

Create a lookup table with summary information on candidate predictors. 

```{r}
ds_smry_ls$predictors_lup <- TTU_predictors_lup(make_pt_TTU_predictors_lup(short_name_chr = ds_smry_ls$candidate_predrs_chr,
                                              long_name_chr = c("K6 total score", "PHQ9 total score"),
                                              min_val_dbl = 0,
                                              max_val_dbl = c(24,27),
                                              class_chr = "integer",
                                              increment_dbl = 1,
                                              class_fn_chr = "integer",
                                              mdl_scaling_dbl = 0.01,
                                              covariate_lgl = F))
```

## Test candidate models, predictors and confounders
Create a lookup table (or as in the below example, use an existing lookup table) with summary information about the types of models we might test.

```{r}
data("mdl_types_lup",package = "TTU") # LUP needs to be a class of TTU
mdl_types_lup
```

Select which models from the lookup table that we wish to compare in this analysis. In this case we select all of the available options.

```{r}
mdl_smry_ls <- list(mdl_types_lup = mdl_types_lup,
                    mdl_types_chr = mdl_types_lup$short_name_chr,
                    choose_from_pfx_chr = c("GLM","OLS","BET"))
```

Set a seed to facilitate reproducibility.

```{r}
seed_1L_int = 12345
set.seed(seed_1L_int)
```

```{r}
bl_tb <- transform_ds_for_tstng(scored_data_tb, 
                                dep_var_nm_1L_chr = ds_smry_ls$dep_var_nm_1L_chr,
                                candidate_predrs_chr = ds_smry_ls$candidate_predrs_chr,
                                dep_var_max_val_1L_dbl = 0.999,
                                round_var_nm_1L_chr = ds_smry_ls$round_var_nm_1L_chr, 
                                round_val_1L_chr = ds_smry_ls$round_bl_val_1L_chr)
bl_tb 
```

Reorder candidate predictors in descending order of correlation with the dependent variable. 

```{r}
ds_smry_ls$candidate_predrs_chr <- reorder_cndt_predrs_chr(ds_smry_ls$candidate_predrs_chr,
        data_tb = bl_tb, dep_var_nm_1L_chr = ds_smry_ls$dep_var_nm_1L_chr)
```

Identify the candidate predictor with the highest correlation. Retrieve its description from the candidate predictors lookup table.

```{r}
mdl_smry_ls$predr_var_nm_1L_chr <- ds_smry_ls$candidate_predrs_chr[1]
mdl_smry_ls$predr_var_desc_1L_chr <- ds_smry_ls$predictors_lup %>% ready4fun::get_from_lup_obj(match_value_xx = mdl_smry_ls$predr_var_nm_1L_chr, match_var_nm_1L_chr = "short_name_chr", target_var_nm_1L_chr = "long_name_chr",
        evaluate_lgl = F)
mdl_smry_ls$predr_var_desc_1L_chr
```

Create a vector of all potential values of the selected predictor.

```{r}
mdl_smry_ls$predr_vals_dbl <- make_predr_vals(mdl_smry_ls$predr_var_nm_1L_chr, candidate_predrs_lup = ds_smry_ls$predictors_lup)
mdl_smry_ls$predr_vals_dbl
```

Compare all candidate model types, each using only the highest correlated candidate predictor (`r predr_var_desc_1L_chr`).

```{r}
mdl_smry_ls$n_folds_1L_int = 10L
mdl_smry_ls$smry_of_sngl_predr_mdls_tb <- write_sngl_predr_multi_mdls_outps(data_tb = bl_tb,
        n_folds_1L_int = mdl_smry_ls$n_folds_1L_int, mdl_types_chr = mdl_smry_ls$mdl_types_chr,
        dep_var_nm_1L_chr = ds_smry_ls$dep_var_nm_1L_chr, predr_var_nm_1L_chr = mdl_smry_ls$predr_var_nm_1L_chr,
        predr_var_desc_1L_chr = mdl_smry_ls$predr_var_nm_1L_chr, predr_vals_dbl = mdl_smry_ls$predr_vals_dbl,
        path_to_write_to_1L_chr = path_to_write_to_1L_chr, new_dir_nm_1L_chr =  "A_Candidate_Mdls_Cmprsns",
        mdl_types_lup = mdl_smry_ls$mdl_types_lup) # Takes more than vignette time limit to render. Need to add and link to report summarising output.
mdl_smry_ls$smry_of_sngl_predr_mdls_tb # Make this a class with a print method
```

Identify the highest performing model in each category of candidate model using [STATE CRITERION].

```{r}
mdl_smry_ls$prefd_mdl_types_chr <- make_prefd_mdls_vec(mdl_smry_ls$smry_of_sngl_predr_mdls_tb,
                                           choose_from_pfx_chr = mdl_smry_ls$choose_from_pfx_chr)
mdl_smry_ls$prefd_mdl_types_chr
```
You can override the selections based on the previous criterion and instead use your own judgment (possibly based on visual inspection of density plots) to specify your preferred model types, in descending order of preference.

```{r}
mdl_smry_ls$prefd_mdl_types_chr <- c("GLM_GSN_LOG","OLS_CLL")
```

Next, compare all of candidate predictors using the most preferred model type.

```{r}
mdl_smry_ls$max_nbr_of_boruta_mdl_runs_int = 300L
mdl_smry_ls$predr_cmprsns_tb <- write_predr_cmprsn_outps(data_tb = bl_tb,
                                             path_to_write_to_1L_chr = path_to_write_to_1L_chr,
                                             new_dir_nm_1L_chr = "B_Candidate_Predrs_Cmprsns",
                                             dep_var_nm_1L_chr = ds_smry_ls$dep_var_nm_1L_chr, 
                                             candidate_predrs_chr = ds_smry_ls$candidate_predrs_chr,
                                             max_nbr_of_boruta_mdl_runs_int = mdl_smry_ls$max_nbr_of_boruta_mdl_runs_int)
mdl_smry_ls$predr_cmprsns_tb # Add report and class with print method

```
Now, prepare a summary table of the performance of each model of the most preferred model type (one model for each candidate predictor).

```{r}
    mdl_smry_ls$smry_of_mdl_sngl_predrs_tb <- write_mdl_type_multi_outps(data_tb = bl_tb,
        n_folds_1L_int = mdl_smry_ls$n_folds_1L_int, predrs_var_nms_chr = mdl_smry_ls$predr_cmprsns_tb$predr_chr,
        mdl_type_1L_chr = mdl_smry_ls$prefd_mdl_types_chr[1], dep_var_nm_1L_chr = ds_smry_ls$dep_var_nm_1L_chr,
        path_to_write_to_1L_chr = path_to_write_to_1L_chr, new_dir_nm_1L_chr = "C_Predrs_Sngl_Mdl_Cmprsns",
        fl_nm_pfx_1L_chr = "C_PREDR", mdl_types_lup = mdl_smry_ls$mdl_types_lup) 
mdl_smry_ls$smry_of_mdl_sngl_predrs_tb # Add report and class with print method
```

We rerun each of these models, but this time add all our candidate covariates to each model. We create a summary table of the performance of each of the updated models.

```{r}
bl_tb <- scored_data_tb %>% transform_ds_for_tstng(candidate_predrs_chr = ds_smry_ls$candidate_predrs_chr,
        covar_var_nms_chr = ds_smry_ls$candidate_covar_nms_chr, remove_all_mssng_1L_lgl = T,
        round_val_1L_chr = ds_smry_ls$round_bl_val_1L_chr)
mdl_smry_ls$mdls_with_covars_smry_tb <- write_mdl_type_covars_mdls(bl_tb,
        dep_var_nm_1L_chr = ds_smry_ls$dep_var_nm_1L_chr, predrs_var_nms_chr = ds_smry_ls$candidate_predrs_chr,
        covar_var_nms_chr = ds_smry_ls$candidate_covar_nms_chr, mdl_type_1L_chr = mdl_smry_ls$prefd_mdl_types_chr[1],
        path_to_write_to_1L_chr = path_to_write_to_1L_chr, new_dir_nm_1L_chr = "D_Predr_Covars_Cmprsn",
        fl_nm_pfx_1L_chr = "D_CT",
        mdl_types_lup = mdl_smry_ls$mdl_types_lup)
mdl_smry_ls$mdls_with_covars_smry_tb # Add report and class with print method. Note negative values
```
Identify which covariates are significant predictors in any of the models.

```{r}
mdl_smry_ls$signt_covars_chr <- get_signft_covars(mdls_with_covars_smry_tb = mdl_smry_ls$mdls_with_covars_smry_tb,
                                      covar_var_nms_chr = ds_smry_ls$candidate_covar_nms_chr) # THIS FN NEEDS FIXING FOR CAT VARS
mdl_smry_ls$signt_covars_chr
```

We can override the covariates to select (in the below example we have opted not to do so and use the significant predictors selected in the previous step).

```{r}
mdl_smry_ls$prefd_covars_chr <- NA_character_
    if (is.na(mdl_smry_ls$prefd_covars_chr))
        mdl_smry_ls$prefd_covars_chr <- mdl_smry_ls$signt_covars_chr
```

```{r}
    empty_tb <- write_mdl_type_multi_outps(data_tb = bl_tb, n_folds_1L_int = NULL,
        start_1L_chr = NA_character_, predrs_var_nms_chr = mdl_smry_ls$predr_cmprsns_tb$predr_chr,
        covar_var_nms_chr = ds_smry_ls$candidate_covar_nms_chr, mdl_type_1L_chr = mdl_smry_ls$prefd_mdl_types_chr[2],
        dep_var_nm_1L_chr = ds_smry_ls$dep_var_nm_1L_chr, path_to_write_to_1L_chr = path_to_write_to_1L_chr,
        new_dir_nm_1L_chr = "E_Predrs_W_Covars_Sngl_Mdl_Cmprsns", mdl_types_lup = mdl_smry_ls$mdl_types_lup, fl_nm_pfx_1L_chr = "E_CK_CV")
    mdl_smry_ls$predr_vars_nms_ls <- make_predr_vars_nms_ls(main_predrs_chr = mdl_smry_ls$predr_cmprsns_tb$predr_chr,
        covars_ls = list(mdl_smry_ls$prefd_covars_chr))
```

```{r}
mdl_smry_ls$mdl_nms_ls <- make_mdl_nms_ls(mdl_smry_ls$predr_vars_nms_ls, mdl_types_chr = mdl_smry_ls$prefd_mdl_types_chr)
```

```{r}
outp_smry_ls <- list(scored_data_tb = scored_data_tb, 
                     smry_of_sngl_predr_mdls_tb = mdl_smry_ls$smry_of_sngl_predr_mdls_tb,
                     prefd_mdl_types_chr = mdl_smry_ls$prefd_mdl_types_chr, 
                     predr_cmprsns_tb = mdl_smry_ls$predr_cmprsns_tb,
                     smry_of_mdl_sngl_predrs_tb = mdl_smry_ls$smry_of_mdl_sngl_predrs_tb,
                     mdls_with_covars_smry_tb = mdl_smry_ls$mdls_with_covars_smry_tb,
                     signt_covars_chr = mdl_smry_ls$signt_covars_chr, 
                     prefd_covars_chr = mdl_smry_ls$prefd_covars_chr,
                     dep_var_nm_1L_chr = ds_smry_ls$dep_var_nm_1L_chr, 
                     predr_vars_nms_ls = mdl_smry_ls$predr_vars_nms_ls,
                     mdl_nms_ls = mdl_smry_ls$mdl_nms_ls, 
                     id_var_nm_1L_chr = ds_smry_ls$id_var_nm_1L_chr,
                     round_var_nm_1L_chr = ds_smry_ls$round_var_nm_1L_chr,
                     round_bl_val_1L_chr = ds_smry_ls$round_bl_val_1L_chr,
                     path_to_write_to_1L_chr = path_to_write_to_1L_chr, 
                     seed_1L_int = seed_1L_int,
                     n_folds_1L_int = mdl_smry_ls$n_folds_1L_int, 
                     max_nbr_of_boruta_mdl_runs_int = mdl_smry_ls$max_nbr_of_boruta_mdl_runs_int,
                     mdl_types_lup = mdl_smry_ls$mdl_types_lup, 
                     file_paths_chr = list.files(path_to_write_to_1L_chr, recursive = T))
```
## Apply selected models to selected predictors
```{r}
outp_smry_ls <- write_ts_mdls_from_alg_outp(outp_smry_ls,
                                            fn_ls = list(fit_gsn_log_lnk,fit_clg_log_tfmn),
                                            backend_1L_chr = "cmdstanr",
                                            iters_1L_int = 500L)
```
## Create shareable version of predictive models
It is not appropriate to share the raw models created in the previous step publicly (as they contain confidential data and are very large in file size). We therefore create shareable versions that are relatively small in file size and contain no confidential data, but that have the coefficients from the original models. 

If you have a Dataverse account you can add details for your account (which will differ from the ones we use for ours below) to the `outp_smry_ls` object. If you do not have  a Dataverse account, do not use the dv_ls argument (or set it to its default value of NULL). 

```{r eval=FALSE}
outp_smry_ls$dv_ls <- list(dv_nm_1L_chr = "firstbounce",
                               ds_url_1L_chr = "https://doi.org/10.7910/DVN/JC6PTV", 
                               parent_dv_dir_1L_chr = "../../../../Data/Dataverse")
```
This following call to `write_shareable_mdls`{.R} writes shareable models to a new subdirectory (G_Shareable) of your nominated output director on your local machine. IF you added details of a Dataverse account in the previous step the function will also push these shareable models to your Dataverse online data repository.

```{r eval=T}
outp_smry_ls <- write_shareable_mdls(outp_smry_ls,
                                     new_dir_nm_1L_chr = "G_Shareable",
                                     shareable_title_detail_1L_chr = "The model that can be used to predict adolescent AQoL6D. Note this model is a placeholder as it has been estimated from synthetic data.")
```

The files created in the following step are available here: https://doi.org/10.7910/DVN/JC6PTV

## Create shareable population data

To aid replication, we can create a purely synthetic dataset, representative of the source data, but containing no real data on any individual.

```{r eval=T}
outp_smry_ls$fk_data_tb <- TTU::make_fake_ts_data(outp_smry_ls)
```

## Save work

Finally, we save a complete record of our analysis.

```{r}
saveRDS(outp_smry_ls,paste0(outp_smry_ls$path_to_write_to_1L_chr,"/I_ALL_OUTPUT_.RDS"))
```
