---
title: "TTU"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TTU}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE, warning=FALSE, results='hide'}
library(TTU)
```

The [ready4 framework model modules](https://www.ready4-dev.com/docs/framework/implementation/modularity/) in TTU are designed to make it easier to implement utility mapping studies for with [ready4 youth mental health economic model](https://www.ready4-dev.com/docs/model/) (or any other model developed with the [ready4 framework](https://www.ready4-dev.com)).

This development version of the TTU package has been made available as part of the process of testing and documenting the package. [Installation instructions are on the package homepage](https://ready4-dev.github.io/TTU/index.html). Currently, one vignette article is available to demonstrate how to use the TTU package:

- [Implement A Utility Mapping Study (Adolescent AQoL-6D Example)](V_01.html)



