---
title: "TTU"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TTU}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TTU)
```
This development version of the TTU package has been made available as part of the process of testing and documenting the package. 

Note that, one of the key functions in TTU (`write_ts_mdls_from_alg_outp`{.R}) makes a call to the Stan program. This function requires that you have the `cmdstanr` package installed on your machine (which should occur automatically when you install TTU) and have performed the necessary configuration of that package (refer to [https://mc-stan.org/cmdstanr/](https://mc-stan.org/cmdstanr/) for details).

The following vignettes demonstrate the two main workflows supported by the TTU package:

- [Exploratory analysis workflow](Model_TTU.html)
- [Analysis, reporting and dissemination workflow](CSP_EQ5D_TTU.html)
