---
title: "Fake Data Generator"
author: "Matthew Hamilton"
date: "11/08/2020"
output: html_document
---

```{r echo = F}
library("magrittr")
library(FBaqol)
```
# Introduction
The workflow illustrated in this vignette outlines steps to generate a purely synthetic (i.e. fake - no trace of any real records) population and is appropriate for when you do not have access to original dataset whose properties you wish your fake data to represent. A different (and simpler) workflow can be implemented when you do have access to the source dataset. Instead of direct access to the original dataset, it is assumed that you have at least some summary data (e.g. means and standard deviations of variables, correlation matrices). Where you do not have all required summary data, you can use assumptions. The more comprehensive the summary data available to you (and the less assumptions you use), the more realistic will be your representation of the original data.


# Specify parameters to generate outcome fake data
The first set of input data are the proportions for each allowed response for each of the twenty AQOL-6D questions at both baseline and followup.

```{r}
aqol_items_props_tbs_ls <- list(bl_answer_props_tb = tibble::tribble(
    ~Question, ~Answer_1, ~Answer_2, ~Answer_3, ~Answer_4, ~Answer_5, ~Answer_6,
    "Q1", 0.35, 0.38, 0.16, 0.03, NA_real_,100, # Check item 5 in real data.
    "Q2", 0.28, 0.38, 0.18, 0.08, 0.04,100,
    "Q3", 0.78, 0.18, 0.03, 0.01, 0.0, 100,
    "Q4", 0.64, 0.23, 0.09, 0.0, 100, NA_real_,
    "Q5", 0.3, 0.48, 0.12, 0.05, 100, NA_real_,
    "Q6", 0.33, 0.48, 0.15, 100, NA_real_,NA_real_,
    "Q7", 0.44, 0.27, 0.11, 100, NA_real_, NA_real_,
    "Q8", 0.18, 0.29, 0.23, 0.21, 100, NA_real_,
    "Q9", 0.07, 0.27, 0.19, 0.37, 100, NA_real_,
    "Q10", 0.04, 0.15, 0.4, 0.25, 100, NA_real_,
    "Q11", 0.03, 0.13, 0.52, 0.25, 100, NA_real_,
    "Q12", 0.06, 0.21, 0.25, 0.34, 100, NA_real_,
    "Q13", 0.05, 0.25, 0.31, 0.28, 100, NA_real_,
    "Q14", 0.05, 0.3, 0.34, 0.25, 100, NA_real_,
    "Q15", 0.57, 0.25, 0.12, 100, NA_real_,NA_real_,
    "Q16", 0.48, 0.42, 0.06, 100, NA_real_, NA_real_,
    "Q17", 0.44, 0.3, 0.16, 0.07, 100, NA_real_,
    "Q18", 0.33, 0.38, 0.25, 0.04, 0.0, 100,
    "Q19", 0.33, 0.49, 0.16, 0.02, 0.0, 100,
    "Q20", 0.67, 0.21, 0.02, 100, NA_real_,NA_real_
  ),
    fup_answer_props_tb = tibble::tribble(
    ~Question, ~Answer_1, ~Answer_2, ~Answer_3, ~Answer_4, ~Answer_5, ~Answer_6,
    "Q1", 0.51, 0.33, 0.12, 0.02, NA_real_, 100,
    "Q2", 0.36, 0.38, 0.16, 0.06, 0.02,100,
    "Q3", 0.81, 0.15, 0.04, 0.00, 0.0, 100,
    "Q4", 0.73, 0.18, 0.09, 0.0, 100, NA_real_,
    "Q5", 0.36, 0.42, 0.12, 0.05, 100, NA_real_,
    "Q6", 0.48, 0.40, 0.11, 100, NA_real_,NA_real_,
    "Q7", 0.57, 0.25, 0.09, 100, NA_real_, NA_real_,
    "Q8", 0.31, 0.33, 0.17, 0.12, 100, NA_real_,
    "Q9", 0.13, 0.35, 0.19, 0.23, 100, NA_real_,
    "Q10", 0.1, 0.21, 0.43, 0.16, 100, NA_real_,
    "Q11", 0.06, 0.25, 0.48, 0.18, 100, NA_real_,
    "Q12", 0.08, 0.27, 0.26, 0.25, 100, NA_real_,
    "Q13", 0.07, 0.37, 0.31, 0.19, 100, NA_real_,
    "Q14", 0.08, 0.37, 0.34, 0.15, 100, NA_real_,
    "Q15", 0.62, 0.23, 0.09, 100, NA_real_,NA_real_,
    "Q16", 0.52, 0.40, 0.06, 100, NA_real_, NA_real_,
    "Q17", 0.51, 0.28, 0.15, 0.06, 100, NA_real_,
    "Q18", 0.37, 0.35, 0.25, 0.03, 0.0, 100,
    "Q19", 0.43, 0.40, 0.16, 0.01, 0.0, 100,
    "Q20", 0.77, 0.21, 0.02, 100, NA_real_,NA_real_
  )) %>%
make_complete_props_tbs_ls()
```

```{r}
aqol_items_props_tbs_ls
```

The next step is to specify the correlations between outcome variables.

```{r}
cor_mat_ls <- list(matrix(c(1,-0.78,0.72,-0.67,-0.71,-0.65,-0.67,
                               NA,1,-0.73,0.69,0.66,0.63,0.71,
                               NA,NA,1,-.57,-0.64,-0.57,-0.65,
                               NA,NA,NA,1,0.74,0.70,0.63,
                               NA,NA,NA,NA,1,0.7,0.59,
                               NA,NA,NA,NA,NA,1,0.55,
                               NA,NA,NA,NA,NA,NA,1),7,7),
                    matrix(c(1,-0.81,0.72,-0.71,-0.73,-0.64,-0.68,
                        NA,1,-0.72,0.69,0.68,0.61,0.68,
                        NA,NA,1,-0.59,-0.61,-0.51,-0.61,
                        NA,NA,NA,1,0.75,0.71,0.6,
                        NA,NA,NA,NA,1,0.68,0.59,
                        NA,NA,NA,NA,NA,1,0.52,
                        NA,NA,NA,NA,NA,NA,1),7,7)) 

```

Finally, we need to specify the univariate distribution parameters for each of the outcome variables.
```{r}
synth_data_spine_ls <- list(cor_mat_ls = cor_mat_ls,
                            nbr_obs_dbl = c(1068,643),
                            timepoint_nms_chr = c("BL","FUP"),
                           means_ls = list(c(0.6,12.8,78.2, 10.4,8.1,34.2,12.2),
                                           c(0.7,9.8,89.4, 7.9,6.3,28.8,9.8)),
                           sds_ls = list(c(0.2,6.6,24.8,5.7,4.7,17.9,5.8),
                                         c(0.2,6.5,24.4,5.5,4.3,17.8,5.9)),
                           missing_ls = list(c(0,4,10,6,7,7,4),
                                             c(0,5,2,2,1,2,2)),
                     min_max_ls = list(c(0.03,1),
                                       c(0,27),
                                       c(0,150),
                                       c(0,21),
                                       c(0,20),
                                       c(0,82),
                                       c(0,24)),
discrete_lgl = c(F,rep(T,6)),
var_names_chr = c("aqol6d_total_w","phq9_total","bads_total","gad7_total",
                     "oasis_total","scared_total","k6_total"),
aqol_tots_var_nms_chr = c(cumulative = "aqol6d_total_c",
                          weighted = "aqol6d_total_w")
) 
aqol_scores_pars_ls <- list(means_dbl = c(44.5,40.6), 
                           sds_dbl = c(9.9,9.8),
                           corr_dbl = -0.95)
```


```{r, results='hide', message=FALSE}
aqol6d_adol_pop_tbs_ls <- make_aqol6d_adol_pop_tbs_ls(aqol_items_props_tbs_ls = aqol_items_props_tbs_ls,
                                        aqol_scores_pars_ls = aqol_scores_pars_ls,
                                        series_names_chr =  c("bl_outcomes_tb","fup_outcomes_tb"),
                                        synth_data_spine_ls = synth_data_spine_ls,
                                        temporal_cors_ls = list(aqol6d_total_w = 0.85))

```

```{r}
## FAKE PLACEHOLDER DATA
descriptives_BL_tb <- tibble::tibble(fkClientID = aqol6d_adol_pop_tbs_ls$bl_outcomes_tb$fkClientID,
                        round = c(1) ,# %>% factor(labels = c("Baseline")),
                        d_age = rnorm(1068,18.1,3.3) %>% 
                          #round(0) %>% 
                          purrr::map_dbl(~min(.x,25) %>% max(12)),
                       #Age_group = NA_character_,
                       d_gender = c(rep(1,653),
                                  rep(2,359),
                                  rep(3,39),
                                  rep(NA_real_,17)) %>% scramble_xx() %>%
                         factor(labels = c("Female","Male","Other")),
                       d_sexual_ori_s = c(rep(1,738),
                                  rep(2,289),
                                  rep(NA_real_,41)) %>% scramble_xx() %>%
                         factor(labels = c("Straight","Other")),
                       Region = c(rep(1,671),
                                  rep(2,397)) %>% scramble_xx() %>%
                         factor(labels = c("Metro","Regional")),
                       CALD = c(rep(T,759),
                                  rep(F,169),
                                  rep(NA,140)) %>% scramble_xx(),
                       d_studying_working = c(rep(1,405),
                                                      rep(2,167),
                                                      rep(3,305),
                                                      rep(4,159),
                                                      rep(NA_real_,32)) %>% scramble_xx() %>% 
                         factor(labels = c("Studying only",
                                           "Working only",
                                           "Studying and working",
                                           "Not studying or working")),
                         c_p_diag_s = c(rep(1,182),
                                                 rep(2,264),
                                                 rep(3,332),
                                                 rep(4,237),
                                                 rep(NA_real_,53)) %>% scramble_xx() %>%
                         factor(labels = c("Depression", "Anxiety","Depression and Anxiety", "Other")),
                         c_clinical_staging_s = c(rep(1,625),
                                  rep(2,326),
                                  rep(3,86),
                                  rep(NA_real_,31)) %>% scramble_xx() %>%
                         factor(labels = c("0-1a","1b","2-4")),
                         c_sofas = c(rnorm(1068-30,65.2,9.5),
                                   rep(NA_real_,30)) %>% 
                         purrr::map_dbl(~min(.x,100) %>% max(0)) %>% 
                         scramble_xx(),
                       s_centre = NA_character_, 
                       d_agegroup = NA_character_,  
                       d_sex_birth_s = NA_character_,   
                       d_country_bir_s = NA_character_, 
                       d_ATSI = NA_character_,
                       d_english_home = NA, 
                       d_english_native = NA, 
                       d_relation_s = c(rep(1,325),
                                  rep(2,426),
                                  rep(3,286),
                                  rep(NA_real_,31)) %>% scramble_xx() %>%
                         factor(labels = c("REPLACE_ME_1","REPLACE_ME_2","REPLACE_ME_3")))  %>%
  dplyr::mutate(d_sex_birth_s = dplyr::case_when(is.na(d_gender) ~ NA_integer_,
                                                 as.integer(d_gender) %in% c(1L,2L) & runif(1068)>0.995 ~ as.integer(d_gender) %>% purrr::map_int(~ifelse(is.na(.x),.x,switch(.x,2L,1L,3L))),
                                                 as.integer(d_gender) ==3 ~ sample(c(1L,2L),1068,replace = T),
                                                 TRUE ~ as.integer(d_gender)
                ) %>%
                  factor(labels = c("Female","Male")))
descriptives_FUP_tb <- descriptives_BL_tb %>% 
  dplyr::filter(fkClientID %in% aqol6d_adol_pop_tbs_ls$fup_outcomes_tb$fkClientID) %>%
  dplyr::mutate(round = 2,
                d_age = d_age + 0.25,
                Region = Region %>% randomise_changes_in_fct_levs(0.98),
                d_studying_working = d_studying_working %>% randomise_changes_in_fct_levs(0.9),
                c_p_diag_s = c_p_diag_s %>% randomise_changes_in_fct_levs(0.90),
                c_clinical_staging_s = c_clinical_staging_s %>% randomise_changes_in_fct_levs(0.8),
                c_sofas = c_sofas + rnorm(643,4.7,10) %>% 
                         purrr::map_dbl(~min(.x,100) %>% max(0)))


```

```{r}
bl_tb <- dplyr::inner_join(descriptives_BL_tb,aqol6d_adol_pop_tbs_ls$bl_outcomes_tb) 
fup_tb <- dplyr::inner_join(descriptives_FUP_tb,aqol6d_adol_pop_tbs_ls$fup_outcomes_tb)
```

```{r}
bl_tb <- bl_tb %>%
  dplyr::mutate(c_sofas = faux::rnorm_pre(bl_tb$aqol6d_total_w %>% as.vector(), mu = 65.2, sd = 9.5, r = 0.5, empirical = T) %>% purrr::map_dbl(~min(.x,100) %>% max(0)))
fup_tb <- fup_tb %>%
  dplyr::mutate(c_sofas = faux::rnorm_pre(fup_tb$aqol6d_total_w %>% as.vector(), mu = 69.9, sd = 10, r = 0.5, empirical = T) %>% purrr::map_dbl(~min(.x,100) %>% max(0)))
```

```{r}
composite_tb <- dplyr::bind_rows(bl_tb,fup_tb) %>%
  dplyr::mutate(d_age = floor(d_age)) %>%
  dplyr::mutate(d_gender = d_gender %>% as.character() %>%
                  purrr::map_chr(~ifelse(.x=="Other",
                                         sample(c("Genderqueer/gender nonconforming/agender",
                                                              "Transgender"),1),
                                         .x)),
                s_centre = Region %>% as.character() %>%
                  purrr::map_chr(~ifelse(.x=="Metro",
                                         sample(c("Canberra","Southport","Knox"),1),
                                         "Regional Centre")),
                d_country_bir_s = CALD %>%
                  purrr::map_chr(~ifelse(.x,
                                         "Other",
                                         "Australia")), 
                       d_ATSI = CALD %>%
                  purrr::map_chr(~ifelse(.x,
                                         "Yes",
                                         "No")),
                       d_english_home = CALD %>%
                  purrr::map_chr(~ifelse(.x,
                                         "No",
                                         "Yes")), 
                       d_english_native = CALD %>%
                  purrr::map_chr(~ifelse(.x,
                                         "No",
                                         "Yes"))
                ) %>%
  dplyr::select(-CALD) %>%
  dplyr::select(-Region)
    
```

```{r}
composite_tb <- composite_tb %>%
  dplyr::select(-setdiff(names(composite_tb)[startsWith(names(composite_tb),"aqol6d_")],names(composite_tb)[startsWith(names(composite_tb),"aqol6d_q")]))
```

Next we write a copy of these input parameters and the synthetic population dataset as CSV files.

```{r}
dss_tb <- write_results_to_csv(synth_data_spine_ls,
                  output_dir_1L_chr = "Data") 
write.csv(composite_tb, file = paste0("Data/fake_pop_tb.csv"),
                                                        row.names = F)
dss_tb <- tibble::add_case(dss_tb,
                           ds_obj_nm_chr = "fake_pop_tb",
                           title_chr = "Synthetic population representative of study participants but containing no trace of source records. The synthetic population was constructed using correlation matrices and summary statistics from the source dataset.")
```

```{r}
# NOT FOR INCLUSION IN VIGNETTE
ready4use::write_fls_to_dv_ds(dss_tb,
                               dv_nm_1L_chr = "ready4models",
                               ds_url_1L_chr = "https://doi.org/10.7910/DVN/GRZRY5",
                               parent_dv_dir_1L_chr = "../../../../../../Data/Dataverse",
                               paths_to_dirs_chr = "Data",
                               inc_fl_types_chr = ".csv")
```


Finally we save an RDS copy of the synthetic dataset.

```{r}
# if(!dir.exists("Data"))
#   dir.create("Data")
# saveRDS(composite_tb,"Data/fake_pop_tb.rds") 
```

