---
title: "AQoL-6D mappign using GLMM with anxiety/depression measurements"
output: html_document:
  toc: yes 
---


```{r}
#load libraries 
library(pacman)
p_load("dplyr", "tidyr","magrittr","reshape2", "ggplot2","gridExtra", "data.table",  "kableExtra", "knitr",  "here","tidyselect","scales", "ggpubr","Hmisc","stringr","psych","corrplot","arsenal","lavaan","semTools","semPlot","sandwich",
"ggalt","viridis", "ggthemes", "caret","brms")

sessionInfo()

```

Check missing

```{r}
# non missing 
table(Baseline_follow[!is.na(Baseline_follow$aqol6d_total_c),]$round)

nrow(Baseline_follow)
```

# Generallized mixed effect 



## Functions 
```{r}

# function for RMSR
rmse <- function(y,yhat){sqrt(mean((yhat-y)^2))}

# function for fitting Gaussian model with log link
Gaussian_log_link<-function(data,var1){
  data<-data.frame(data)
  #prepare data
    data<-data %>% 
    dplyr::select("aqol6d_total_w","fkClientID","round",var1) %>% 
    dplyr::group_by(fkClientID) %>% 
    dplyr::arrange(fkClientID,round) %>% 
    dplyr::mutate(!!paste0(var1,"_baseline") :=  first(!!as.name(var1))/100) %>% 
    dplyr::mutate(!!paste0(var1,"_change") :=ifelse(round=="Baseline",0,(!!as.name(var1)-lag(!!as.name(var1)))/100))  %>% 
    dplyr::mutate(aqol6d_total_w_cloglog= log(-log(1-ifelse(aqol6d_total_w==1,0.999,aqol6d_total_w)))) %>% 
    na.omit() 
  
  #Bayes models
  brm_model <- brm(formula = as.formula(paste0("aqol6d_total_w ~ ",var1,"_baseline + ",var1,"_change + (1|fkClientID)")), data = data,
                   family = gaussian(link="log"), iter = 4000,seed=1000)
  #print results
  print(plot(brm_model))
  print(summary(brm_model, digits = 4))
  
  #save prediction
  set.seed(23456)
  predictions<-predict(brm_model,summary=F)
  
  # summary statistics for posterior coef, R2, RMSR and Sigma  
  coef<-summary(brm_model, digits = 4)$fixed[2:3,1:4]
  R2<-bayes_R2(brm_model)
  RMSE<-psych::describe( apply(predictions,1,rmse,y=data$aqol6d_total_w),
                                 quant=c(.25,.75),skew = F, ranges = F )
  RMSE <- cbind(RMSE$mean,RMSE$sd,RMSE$Q0.25,RMSE$Q0.75)
  Sigma<-summary(brm_model, digits = 4)$spec_par[1:4]
  
  #combine results
  result<-data.frame(round(rbind(coef,R2,RMSE,Sigma),3))  %>% 
    mutate(Parameter=c(paste(var1," baseline"), paste(var1," change"), 
                       "R2", "RMSE", "Sigma"),
           Model= paste(var1, " model")) %>% 
    mutate(`95% CI`= paste(`l.95..CI`,",", `u.95..CI`)) %>% 
    rename (SE=Est.Error) %>% 
    dplyr::select(Model,Parameter,Estimate,  SE, `95% CI`)
    
  #extract plot
  set.seed(23456)
  data$Predicted<-predict(brm_model)[,1]
  print(data %>% 
        mutate(Observed=aqol6d_total_w) %>% 
        gather(variable, value, Predicted, Observed) %>%
        ggplot(aes(x = value, fill = variable)) +
        geom_bkde(alpha=0.5) +
        geom_rug() +
        scale_fill_viridis( discrete = TRUE) +
        theme_bw() + 
        theme(legend.position="bottom") +
        labs( x="AQoL-6D utility score",y="Density", fill=""))

  print(ggplot(data) + 
      geom_point(aes(x=aqol6d_total_w,y=Predicted,col=round),size=1) +
      theme_bw()  + xlim(0,1)  + ylim(0,1)  + scale_color_manual(values=c("#D55E00","#56B4E9"))  +
      labs( x="Observed AQoL-6D utility score",y="Predicted AQoL-6D utility score", col="") +
      theme(legend.position="bottom"))
  return(result)
  
}

# function for RMSR
rmse_trans <- function(y,yhat){sqrt(mean((1-exp(-exp(yhat))-y)^2))}
# function for fitting Gaussian model with log link
Cloglog_transform<-function(data,var1 ){
  data<-data.frame(data)
  #prepare data
  data<-data %>% 
    dplyr::select("aqol6d_total_w","fkClientID","round",var1) %>% 
    dplyr::group_by(fkClientID) %>% 
    dplyr::arrange(fkClientID,round) %>% 
    dplyr::mutate(!!paste0(var1,"_baseline") :=  first(!!as.name(var1))/100) %>% 
    dplyr::mutate(!!paste0(var1,"_change") :=ifelse(round=="Baseline",0,(!!as.name(var1)-lag(!!as.name(var1)))/100))  %>% 
    dplyr::mutate(aqol6d_total_w_cloglog= log(-log(1-ifelse(aqol6d_total_w==1,0.999,aqol6d_total_w)))) %>% 
    na.omit() 
  
  #Bayes models
  brm_model <- brm(formula = as.formula(paste0("aqol6d_total_w_cloglog ~ ",var1,"_baseline + ",var1,"_change + (1|fkClientID)")), data = data,
                   family = gaussian(link="identity"), iter = 4000,seed=1000)
  #print results
  print(plot(brm_model))
  print(summary(brm_model, digits = 4))
  
  #save prediction
  set.seed(23456)
  predictions<-predict(brm_model,summary=F)
  
  # summary statistics for posterior coef, R2, RMSR and Sigma  
  coef<-summary(brm_model, digits = 4)$fixed[2:3,1:4]
  R2<-bayes_R2(brm_model)
  RMSE<-psych::describe( apply(predictions,1,rmse_trans,y=data$aqol6d_total_w),
                                 quant=c(.25,.75),skew = F, ranges = F )
  RMSE <- cbind(RMSE$mean,RMSE$sd,RMSE$Q0.25,RMSE$Q0.75)
  Sigma<-summary(brm_model, digits = 4)$spec_par[1:4]
  
  #combine results
  result<-data.frame(round(rbind(coef,R2,RMSE,Sigma),3))  %>% 
    mutate(Parameter=c(paste(var1," baseline"), paste(var1," change"), 
                       "R2", "RMSE", "Sigma"),
           Model= paste(var1, " model")) %>% 
    mutate(`95% CI`= paste(`l.95..CI`,",", `u.95..CI`)) %>% 
    rename (SE=Est.Error) %>% 
    dplyr::select(Model,Parameter,Estimate,  SE, `95% CI`)
    
  #extract plot
  set.seed(23456)
  data$Predicted<-1-exp(-exp(predict(brm_model)[,1]))
  
  print(data %>% 
        mutate(Observed=aqol6d_total_w) %>% 
        gather(variable, value, Predicted, Observed) %>%
        ggplot(aes(x = value, fill = variable)) +
        geom_bkde(alpha=0.5) +
        geom_rug() +
        scale_fill_viridis( discrete = TRUE) +
        theme_bw() + 
        theme(legend.position="bottom") +
        labs( x="AQoL-6D utility score",y="Density", fill=""))

  print(ggplot(data) + 
      geom_jitter(aes(x=aqol6d_total_w,y=Predicted,col=round),size=1,alpha=0.7) +
      theme_bw()  + xlim(0,1)  + ylim(0,1)  + scale_color_manual(values=c("#D55E00","#56B4E9"))  +
      labs( x="Observed AQoL-6D utility score",y="Predicted AQoL-6D utility score", col="") +
      theme(legend.position="bottom"))
  return(result)
  
}

```


## PHQ9 

### Gaussian with log link

```{r}
model1<-Gaussian_log_link(Baseline_follow,"PHQ9")
```

### Cloglog transformed AQoL-6D scores

```{r}
model2<-Cloglog_transform(Baseline_follow,"PHQ9")
```

```{r}
results<-cbind(model1,model2)
```


## BADS 

### Gaussian with log link

```{r}
model1<-Gaussian_log_link(Baseline_follow,"BADS")

```

### Cloglog transformed AQoL-6D scores

```{r}
model2<-Cloglog_transform(Baseline_follow,"BADS")
```

```{r}
results<-rbind(results,cbind(model1,model2))
```


## GAD7 

### Gaussian with log link

```{r}
model1<-Gaussian_log_link(Baseline_follow,"GAD7")
```

### Cloglog transformed AQoL-6D scores

```{r}
model2<-Cloglog_transform(Baseline_follow,"GAD7")
```

```{r}
results<-rbind(results,cbind(model1,model2))
```



## OASIS

### Gaussian with log link

```{r}
model1<-Gaussian_log_link(Baseline_follow,"OASIS")

```

### Cloglog transformed AQoL-6D scores

```{r}
model2<-Cloglog_transform(Baseline_follow,"OASIS")
```

```{r}
results<-rbind(results,cbind(model1,model2))
```



## SCARED

### Gaussian with log link

```{r}
model1<-Gaussian_log_link(Baseline_follow,"SCARED")

```

### Cloglog transformed AQoL-6D scores

```{r}
model2<-Cloglog_transform(Baseline_follow,"SCARED")
```

```{r}
results<-rbind(results,cbind(model1,model2))
```



## K6

### Gaussian with log link

```{r}
model1<-Gaussian_log_link(Baseline_follow,"K6")

```

### Cloglog transformed AQoL-6D scores

```{r}
model2<-Cloglog_transform(Baseline_follow,"K6")
```

```{r}
results<-rbind(results,cbind(model1,model2))
```


## Summary table 

```{r}
knitr::kable( results[,c(1:5,8:10)]  , format="html") %>%
    kable_styling(bootstrap_options = "striped", full_width = F) %>%  
    add_header_above(c(" " = 2, "GLM (Gaussian distribution with log link)" = 3, "OLS (cloglog transformed utility score)" = 3))
```


