---
title: "_Test_Cndt_Mdls_Predrs_And_Covars"
author: "Matthew Hamilton & Caroline Gao"
date: "23/03/2021"
output: html_document
---

The sequence of commands in this step test which models, predictors and covariates perform best. 

Compare model types using most correlated predictor.

```{r message=FALSE, results='hide', warning=FALSE}
cmprsns_ls <- TTU::write_mdl_cmprsn(scored_data_tb = data_tb,
                                ds_smry_ls = ds_smry_ls,
                                mdl_smry_ls = mdl_smry_ls,
                                output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                seed_1L_int = params_ls$seed_1L_int)

```

Select preferred model types.

```{r echo = !is.null(params_ls$prefd_mdl_types_chr), eval= !is.null(params_ls$prefd_mdl_types_chr), message=FALSE, results='hide', warning=FALSE}
if(!is.null(params_ls$prefd_mdl_types_chr)){
  cmprsns_ls$mdl_smry_ls$prefd_mdl_types_chr <- params_ls$prefd_mdl_types_chr
}
```

Compare candidate predictors and covariates using most preferred model type.

```{r message=FALSE, results='hide', warning=FALSE}
cmprsns_ls <- TTU::write_predr_and_covars_cmprsn(scored_data_tb = data_tb,
                                           bl_tb = cmprsns_ls$bl_tb,
                                           ds_smry_ls = cmprsns_ls$ds_smry_ls,
                                           mdl_smry_ls  = cmprsns_ls$mdl_smry_ls,
                                           output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                           seed_1L_int = params_ls$seed_1L_int)
```

`r ifelse(!is.null(params_ls$prefd_covars_chr),"Specify the covariates to include.","")`

```{r echo = !is.null(params_ls$prefd_covars_chr), eval = !is.null(params_ls$prefd_covars_chr), message=FALSE, results='hide', warning=FALSE}
if(!is.null(params_ls$prefd_covars_chr)){
  cmprsns_ls$mdl_smry_ls$prefd_covars_chr <- params_ls$prefd_covars_chr
}
```

Compare selected models with selected predictors and selected covariates.

```{r message=FALSE, results='hide', warning=FALSE, fig.show ='hide'}
outp_smry_ls <- TTU::write_mdls_with_covars_cmprsn(scored_data_tb = data_tb,
                                           bl_tb = cmprsns_ls$bl_tb,
                                           ds_smry_ls = cmprsns_ls$ds_smry_ls,
                                           mdl_smry_ls = cmprsns_ls$mdl_smry_ls,
                                           output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                           seed_1L_int = params_ls$seed_1L_int,
                                           session_data_ls = session_data_ls)
```

