---
output: 
  bookdown::pdf_document2: 
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=Header/header_common.yaml"
      - '--lua-filter=Filters/scholarly-metadata.lua'
      - '--lua-filter=Filters/author-info-blocks.lua'
    toc: no
  bookdown::pdf_book: 
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=Header/header_common.yaml"
      - '--lua-filter=Filters/scholarly-metadata.lua'
      - '--lua-filter=Filters/author-info-blocks.lua'
  bookdown::html_document2:
    pandoc_args: 
      - "--metadata-file=Header/header_common.yaml"
      - '--lua-filter=Filters/scholarly-metadata.lua'
      - '--lua-filter=Filters/author-info-blocks.lua' 
    toc: yes
  bookdown::markdown_document2:
    base_format: "officedown::rdocx_document"
    number_sections: yes
    toc: yes
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
        style: Table Caption
        pre: 'Table '
        sep: ': '
      conditional:
        first_row: true
        first_column: false
        last_row: false
        last_column: false
        no_hband: false
        no_vband: true
    pandoc_args: 
      - "--metadata-file=Header/header_common.yaml"
      - '--lua-filter=Filters/scholarly-metadata.lua'
      - '--lua-filter=Filters/author-info-blocks.lua'
      - '--lua-filter=Filters/pagebreaks.lua'
params:
  existing_predrs_ls: !r NULL
  outp_smry_ls: !r NULL
  output_type_1L_chr: HTML
  rltv_path_to_data_dir_1L_chr: ../Output/F_TS_Mdls
  subtitle_1L_chr: "Catalogue of longitudinal models"
  root_dir_1L_chr: ./
  section_type_1L_chr: "#"
subtitle: "`r params$subtitle_1L_chr`"
date: "`r format.Date(Sys.Date(),'%B %d, %Y')`"
graphics: yes
---

```{r setup, include=FALSE}
library(TTU)
library(magrittr)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(root.dir = params$root_dir_1L_chr)
options(tinytex.verbose = TRUE)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
```

```{r include=FALSE}
params_ls <- params
```

```{r echo=FALSE}
predr_vars_nms_ls <- make_predr_vars_nms_ls(main_predrs_chr = params_ls$outp_smry_ls$predr_cmprsn_tb$predr_chr, 
                       covars_ls = list(params_ls$outp_smry_ls$prefd_covars_chr),
                       existing_predrs_ls = params_ls$existing_predrs_ls)
knit_pars_ls <- make_knit_pars_ls(rltv_path_to_data_dir_1L_chr = params_ls$rltv_path_to_data_dir_1L_chr,
                  mdl_types_chr = params_ls$outp_smry_ls$prefd_mdl_types_chr,
                  predr_vars_nms_ls = predr_vars_nms_ls,
                  mdl_types_lup = params_ls$outp_smry_ls$mdl_types_lup, 
                  plt_types_lup = TTU::plt_types_lup,
                  output_type_1L_chr = params_ls$output_type_1L_chr,
                  section_type_1L_chr = params_ls$section_type_1L_chr) 
```

This algorithm authored report summarises a number of longitudinal models for predicting  `r ready4fun::get_from_lup_obj(params_ls$outp_smry_ls$dictionary_tb,                      match_value_xx = params_ls$outp_smry_ls$depnt_var_nm_1L_chr,                                                                  match_var_nm_1L_chr = "var_nm_chr",                                                                  target_var_nm_1L_chr = "var_desc_chr",                                                                  evaluate_lgl = F)` at two time-points. The descriptions of each model included in the report detail model predictor variables, parameter values and predictive performance. Report figures graphically illustrate the predictive performance of models when mean or sampled parameter values are used, with and without transformation of model outputs to enforce within range predictions. A number of these plots compare the performance of predictions when the original R model object (of class *brmsfit*) is used or when predictions are made from a summary table of model coefficients. Each model description also includes a catalogue reference number that is useful for retrieving the model data required to make predictions.

```{r, echo=FALSE, results='asis'}
 knit_pars_ls %>%
  purrr::walk(~knit_mdl_rprt(.x, path_to_mdl_rprt_tmpl_1L_chr = "_mdl_rpt_tmpl.Rmd"))
```
