---
output: 
  bookdown::pdf_document2:
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=Header/header_common.yaml"
      - '--lua-filter=Filters/scholarly-metadata.lua'
      - '--lua-filter=Filters/author-info-blocks.lua'
    toc: no
subtitle: "Methods Report 1: Complete Study Program"
---
<!-- This is a template that you can adapt to use the reporting workflow tools of the TTU package. You should review the vignettes at https://ready4-dev.github.io/TTU/index.html to better understand each step. -->

<!---Do not modify this block. The code blocks in this document are not to be run when knitting this document.--->
```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = F)
```
\blandscape
<!---BLOCK_LANDSCAPE_START--->

```{r message=FALSE}
library(TTU)
```

# Input parameters

## Reporting parameters

### Bibliograhic data
<!-- Un-comment and edit the code chunk below with details on your authorship team. -->
```{r}
# authors_tb <- ready4show::ready4_authors_lup() %>%
#   tibble::add_case(first_nm_chr = "Alejandra",
#                    middle_nm_chr = "Rocio",
#                    last_nm_chr = "Scienceace",
#                    title_chr = "Dr",
#                    qualifications_chr = "MD, PhD",
#                    institute_chr = "Insitute_A, Institute_B",
#                    sequence_int = 1,
#                    is_corresponding_lgl = T,
#                    email_chr = "fake_email@fake_institute.com") %>%
#     tibble::add_case(first_nm_chr = "Fionn",
#                    middle_nm_chr = "Seamus",
#                    last_nm_chr = "Researchchamp",
#                    title_chr = "Prof",
#                    qualifications_chr = "MSc, PhD",
#                    institute_chr = "Insitute_C, Institute_B",
#                    sequence_int = 2,
#                    email_chr = "fake_email@fake_institute.com")
```
<!-- Un-comment and edit the code chunk below with details on your authorship team's institutes. The names supplied to the short_name_chr argument must correspond with values in the institute_chr column of the authors lookup table created in the previous step. -->
```{r}
# institutes_tb <- ready4show::ready4_institutes_lup() %>%
#   tibble::add_case(short_name_chr = "Institute_A", long_name_chr = "Awesome University, Shanghai") %>%
#   tibble::add_case(short_name_chr = "Institute_B", long_name_chr = "August Institution, London") %>%
#   tibble::add_case(short_name_chr = "Institute_C", long_name_chr = "Highly Ranked Uni, Montreal")
```
<!-- Un-comment and edit the code chunk below with details on the title and keywords for your study. -->
```{r}
# header_yaml_args_ls <- make_header_yaml_args_ls(authors_tb = authors_tb,
#                                                 institutes_tb = institutes_tb,
#                                                 title_1L_chr = "A hypothetical study using fake data for instructional purposes only",
#                                                 keywords_chr = c("this","is","a","replication","using","fake","data","do", "not","cite"))
```

### Report formatting
<!-- Un-comment and edit the code chunk below with details on the desired output formats for the scientific manuscript and supplementary reports and the number of digits of decimal extension that will be used when reporting numbers. -->
```{r}
# output_format_ls <- make_output_format_ls(manuscript_outp_1L_chr = "PDF",
#                                           manuscript_digits_1L_int = 2L,
#                                           supplementary_outp_1L_chr = "PDF",
#                                           supplementary_digits_1L_int = 2L)
```

## Data parameters

### Dataset
<!-- Un-comment and edit the code chunk below, replacing the fake dataset details with a command to read in your own data. -->
```{r message=FALSE}
# ds_tb <- youthvars::replication_popl_tb %>% 
#             youthvars::transform_raw_ds_for_analysis() 
```

### Data dictionary
<!-- Un-comment and edit the code chunk below, replacing the default data dictionary with with a command to read in or create a dictionary for your data. The data dictionary must be of the class ready4_dictionary from the ready4use package. -->
```{r}
# dictionary_tb <- youthvars::make_final_rpln_ds_dict()
```

### Dataset metadata
<!-- Un-comment and edit the code chunk below, to specify the relevant meta-data for your dataset. -->
```{r}
# ds_descvs_ls <- make_ds_descvs_ls(candidate_predrs_chr = c("K6","PHQ9"),
#                                   candidate_covar_nms_chr = c("d_age", "SOFAS",
#                                                               "c_p_diag_s",
#                                                               "c_clinical_staging_s"),
#                                   cohort_descv_var_nms_chr = c("d_age",
#                                                                "d_relation_s",
#                                                                "d_studying_working",
#                                                                "c_p_diag_s",
#                                                                "c_clinical_staging_s",
#                                                                "SOFAS"),
#                                   dictionary_tb = dictionary_tb, 
#                                   id_var_nm_1L_chr = "fkClientID", 
#                                   is_fake_1L_lgl = T,
#                                   msrmnt_date_var_nm_1L_chr = "d_interview_date",
#                                   round_var_nm_1L_chr = "round", 
#                                   round_vals_chr = c("Baseline", "Follow-up"),
#                                   maui_item_pfx_1L_chr = "aqol6d_q", 
#                                   utl_wtd_var_nm_1L_chr = "aqol6d_total_w", 
#                                   utl_unwtd_var_nm_1L_chr = "aqol6d_total_c")
```

### Candidate predictors metadata
<!-- Un-comment and edit the code chunk below, to specify additional detail on the candidate predictors (as well as any covariates that will be used in the final models) for your dataset. -->
```{r}
# predictors_lup <- make_pt_TTU_predictors_lup(short_name_chr = c(ds_descvs_ls$candidate_predrs_chr, "SOFAS"),
#                                               long_name_chr = c("K6 total score", "PHQ9 total score", "SOFAS total score"),
#                                               min_val_dbl = 0,
#                                               max_val_dbl = c(24,27,100),
#                                               class_chr = "integer",
#                                               increment_dbl = 1,
#                                               class_fn_chr = c("youthvars::youthvars_k6",
#                                                                "youthvars::youthvars_phq9",
#                                                                "youthvars::youthvars_sofas"),
#                                               mdl_scaling_dbl = 0.01,
#                                               covariate_lgl = F) %>%
#   TTU_predictors_lup()
```

### Multi-Attribute Utility Instrument (MAUI) parameters
<!-- Un-comment and edit the code chunk below, to specify relevant detail on the multi-attibute utility instrument being used in your study. You may need to write a function fto pass to the maui_scoring_fn argument if such a function does not already exist.-->
```{r}
# maui_params_ls <- make_maui_params_ls(maui_domains_pfcs_1L_chr = "vD",
#                                       maui_itm_short_nms_chr = c("Household tasks",
#                                                                  "Getting around","Morbility",
#                                                                  "Self care","Enjoy close rels",
#                                                                  "Family rels", 
#                                                                  "Community involvement", "Despair", 
#                                                                  "Worry", "Sad", "Agitated",
#                                                                  "Energy level","Control",
#                                                                  "Coping","Frequency of pain", 
#                                                                  "Degree of pain",
#                                                                  "Pain interference", "Vision",
#                                                                  "Hearing", "Communication"),
#                                       maui_scoring_fn = youthvars::add_adol6d_scores,
#                                       short_and_long_nm = c("AQoL-6D",
#                                                             "Assessment of Quality of Life - Six Dimension"),
#                                       utl_min_val_1L_dbl = 0.03)
```

## Analysis parameters
<!-- IF YOU PLAN SECONDARY ANALYSES, un-comment and edit the code chunk below as appropriate.-->
```{r}
# scndry_anlys_params_ls <- make_scndry_anlys_params(candidate_predrs_chr = c("SOFAS"),
#                                                    prefd_covars_chr = NA_character_)
```
<!-- Un-comment and edit the code chunk below to define the final input paramters list. Note, you will need to supply values relating to a dataverse that you control to the dv_ds_nm_and_url_chr argument, or else assign a NULL value to this argument. -->
```{r}
# input_params_ls <- make_input_params(ds_tb,
#                                      ds_descvs_ls = ds_descvs_ls,
#                                      dv_ds_nm_and_url_chr = c("fakes", 
#                                                               "https://doi.org/10.7910/DVN/D74QMP"), 
#                                      header_yaml_args_ls = header_yaml_args_ls,
#                                      maui_params_ls = maui_params_ls,
#                                      output_format_ls = output_format_ls,
#                                      predictors_lup = predictors_lup,
#                                      prefd_covars_chr = "SOFAS",
#                                      prefd_mdl_types_chr = c("OLS_CLL","GLM_GSN_LOG"),
#                                      scndry_anlys_params_ls = scndry_anlys_params_ls)
```

# Analyse, Report and Share

## Run analysis
```{r}
write_analyses(input_params_ls)
```

## Report results
```{r}
input_params_ls <- write_mdl_smry_rprt(input_params_ls,
                                       use_shareable_mdls_1L_lgl = T)
```

## Share results
```{r}
write_study_outp_ds(input_params_ls)
```

# Create manuscript

## Create study metadata
<!-- Un-comment and edit the code chunk below as appropriate. You will need to supply values relating to a dataverse you control to the dv_ds_nm_and_url_chr argument, or else assign a NULL value to this argument. -->
```{r}
# input_params_ls <- make_study_descs_ls(input_params_ls = input_params_ls,
#                                        background_1L_chr = "Our study is entirely fictional and has been created to illustrate TTU package functionality.",
#                                        coi_1L_chr = "None declared.",
#                                        conclusion_1L_chr = "If this study was real, the results would be interesting.",
#                                        ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
#                                        funding_1L_chr = "The study was funded by Generous Benefactor.",
#                                        sample_desc_1L_chr = "The study sample is fake data that pretends to be young people aged 12 to 25 years who attended Australian primary care services for mental health related needs between November 2019 to August 2020.",
#                                        time_btwn_bl_and_fup_1L_chr = "three months",
#                                        var_nm_change_lup = tibble::tibble(old_nms_chr = c("PHQ9","GAD7"),
#                                                                           new_nms_chr = c("PHQ-9",
#                                                                                           "GAD-7")))
```

## Render auto-generated first-draft
<!-- Note, if you are not planning on developing the auto-generated scientific summary further with a view to future publication, you can add write_to_dv_1L_lgl = T to the following call, which will save the auto-generated manuscript to your dataverse dataset. -->
```{r}
results_ls <- write_manuscript(input_params_ls = input_params_ls)
```

# Purge dataset copies
```{r}
write_to_delete_ds_copies(results_ls)
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->
